
# Experiment 2: Mutual Exclusivity Effect and Familiarity

In Experiment 2, we used the same design as in the Novel-Novel trials from Experiment 1, but manipulated the amount of  exposure children were given to the novel object and label prior to the critical ME trial. We reasoned that children who observed more instances of a novel label referring to a novel object should have higher certainty about the label name. If the strength of  knowledge about the "familiar" object influences the strength of the ME effect, then we should expect a larger ME effect when the "familiar" object has been labeled more frequently. We find a pattern consistent with this prediction. 

```{r}
EXP2_DATA_PATH <- here("data/2_exp_data.csv")

exp2 <- read_csv(EXP2_DATA_PATH)  %>%
  mutate(age_group = floor(age_mo/12),
         err_type = ifelse(is.na(correct), "no choice", err_type), 
         err = ifelse(is.na(correct), 1, err))
```

## Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

### Participants

```{r}
e2_subs <- exp2 %>%
    mutate(age_group = as.factor(age_group),
          age_group = fct_recode(age_group,
                                "2-yo" = "2",
                                "3-yo" = "3",
                                "4-yo" = "4")) %>%
  group_by(sub_num, age_group) %>%
  summarise(age_mo = age_mo[1], 
            n = n(), 
            err = sum(err)) 

e2_demos <- e2_subs %>%
  group_by(age_group) %>%
  summarise(mean_age = round(mean(age_mo),2), 
            n = n()) %>%
  mutate_at(vars(n, age_group), as.character)

colnames(e2_demos) <- c("Age group", "Mean age (months)", "Sample size")
```

```{r, results = "asis"}
apa_table(e2_demos, caption = "Demographics of children in Experiment 2.")
```

We planned a total sample of 108 children, 12 per between-subjects labeling condition, and 36 total in each one-year age group (see Table 5). Our final sample was `r nrow(e2_subs)` children, ages `r min(e2_subs$age_mo)` -- `r max(e2_subs$age_mo)` months, recruited from the floor of the Boston Children's Museum. Children were randomly assigned to the one-label, two-label, or three label condition, with the total number of children in each age group and condition ranging between 10 and 13.  

### Stimuli

The referent objects were the set of 8 novel objects used in @de_Marchena_2011, consisting of unusual household items (e.g., a yellow plastic drain catcher) or other small, lab-constructed stimuli (e.g., a plastic lid glued to a popsicle stick). All items were distinct in color and shape. The novel words were 8 single syllable  labels (e.g., "dax," "zot," and "gup").

### Design and Procedure

Each child completed four trials. Each trial consisted of a training and a test phase in a "novel-novel" ME task [@de_Marchena_2011]. In the training phase, the experimenter presented the child with a novel object, and explicitly labeled the object with a novel label 1, 2, or 3 times ("Look at the *dax*"), and contrasted it with a second novel object ("And this one is cool too") to ensure equal familiarity. In the test phase, the child was asked to point to the object referred to by a second novel label ("Can you show me the *zot*?"). Number of labels used in the training phase was manipulated between subjects. Object presentation side, object, and word were counterbalanced across children. 

### Data analysis

```{r}
exclusions <- exp2 %>%
  filter(err == 1) %>%
  count(err_type) 

e2_clean <- filter(exp2, !err)
```


We followed the same analytic approach as we registered in Experiment 1, though data were collected chronologically earlier for Experiment 2. Responses were coded as correct if participants selected the novel object at test. A small number of trials were coded as having parent or sibling interference (*N* = `r filter(exclusions, err_type == "interference")$n`), experimenter error (*N* = `r filter(exclusions, err_type == "exp err")$n`), or a child who recognized the target object (*N* = `r filter(exclusions, err_type == "recog obj")$n`), chose both objects (*N* = `r filter(exclusions, err_type == "changed mind")$n`) or did not make a choice (*N* = `r filter(exclusions, err_type == "no choice")$n`). These trials were excluded from further analyses; all trials were removed for two children for whom there was parent or sibling interference on every trial. We centered both age and number of labels for interpretability of coefficients.  The analysis we report here is consistent with that used in @lewis2013b, though there are some slight numerical differences due to reclassification of exclusions. 

## Results and Discussion

Children showed a stronger ME effect with development and as the number of training labels increased (Figure 6).

```{r, fig.width=5, fig.height =3.5, fig.pos = "!t", fig.cap = "Accuracy data for three age groups across three different conditions in Experiment 2. Conditions varied by the number of times the child observed an unambiguous novel label applied to the familiar object prior to the critical ME trial. The dashed line corresponds to chance. Ranges are 95\\% confidence intervals. Points are jittered along the x-axis for visibility."}
mss <- e2_clean %>%
  group_by(age_group, cond, sub_num) %>%
  summarise(correct = mean(correct)) 

ms <- mss %>%
  multi_boot_standard(col = "correct", na.rm=TRUE)

ggplot(ms, aes(x = factor(age_group), y = mean, col = cond)) + 
  geom_hline(yintercept = .5, lty = 2) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(aes(group = cond)) +
  xlab("Age (years)") + 
  ylim(0,1) + 
  ylab("Proportion correct") + 
  scale_color_solarized(name = "Condition", 
                        labels = c("1 label", "2 label", "3 label")) + 
  theme_classic() +
  ggtitle("Experiment 2")

```

```{r}
e2_clean$age_mo_c <- scale(e2_clean$age_mo, 
                           scale = FALSE, center = TRUE)
e2_clean$times_labeled_c <- scale(e2_clean$times_labeled, 
                                  scale = FALSE, center = TRUE)

m3 <- glmer(correct ~ age_mo_c * times_labeled_c  + 
               (times_labeled_c | sub_num), 
      family = "binomial", 
      data = e2_clean) %>%
      summary()

print_model3 <- m3$coefficients %>%
  data.frame() %>%
  stats::setNames(c("B", "SE", "Z", "p")) %>%
  rownames_to_column("term")  %>%
  mutate_at(2:5, function(x) {round(x, 2)}) %>%
  mutate(p_print = ifelse(p == 0, "< .001", p),
         pp_print = ifelse(p == 0, "< .001", paste0("= ", p)),
         pretty_model = paste0("B = ", B, ", SE = ", SE, 
                               ", Z = ", Z, ", p ", pp_print),
        term = c("(Intercept)",
                  "Age",
                  "Num. Labels Observed",
                  "Age x Num. Labels Observed")) %>%
  select(-p) %>%
  rename(p = "p_print") %>%
  select(term, everything(), -pp_print, -pretty_model)
```

```{r, results = "asis"}
apa_table(print_model3, caption = "Parameters of logistic mixed model predicting accuracy on ME trials as a function of age (months) and number of times the child observed a label for the familiar object.")

```

We analyzed the results using a logistic mixed model to predict correct responses with age, number of labels, and their interaction as fixed effects.\footnote{The model specification was as follows:  \texttt{accuracy  $\sim$ times.labeled $*$ age  + (times.labeled~\textbar~subject.id).}} Model results are shown in Table 6. There was a significant effect of both age and number of labels: Children who were older and observed the occurrences of label for the "familiar" object showed stronger ME effect. The interaction between age and number of labels was not significant.

Experiment 2 thus provides causal evidence for a link between the strength of knowledge about the "familiar" word in the ME task and the strength of the ME effect: A stronger representation about the "familiar" word in the ME task leads to a stronger ME inference. This pattern of findings is consistent with the correlational relationship observed in Experiment 1 in which children with larger vocabularies tended to show a larger ME effect. We cannot, however, compare the magnitude of the effects in the two experiments since a few exposures to a novel label in the laboratory is not straight-forwardly comparable to the history of labeling experiences that a child encounters in their natural environment. Nevertheless, Experiment 2 provides strong evidence that at least part of the relationship between vocabulary size and the strength of the ME effect observed in Experiment 1 is due to children's knowledge about  the familiar object label.
