---
title: ME MA exploration for paper
author: Molly Lewis
subtitle: 
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: cerulean
---

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}

library(knitr)
library(tidyverse)
library(lubridate)
library(langcog)
library(corrr)
library(feather)
library(metafor)
library(broom)
library(modelr)

opts_chunk$set(echo = F, message = F, warning = F, 
               error = F, cache = F, tidy = F)


#theme_set(theme_minimal())
source("../scripts/synthesis_helpers.R")
source("../scripts/pcurve.R")
```

```{r}
ma_raw <- read_feather("../../data/mutual_exclusivity") %>%
  select(c(1, 3, 6, 9, 12, 14, 15, 18, 20, 22:24, 26,
           29:30, 49, 51:53, 95:99, 100, 102:103)) %>%
  mutate_if(is.character, as.factor)

AVG_MONTH <- 30.43688

ma_c <- ma_raw %>%
  filter(!is.na(d_calc)) %>%
  mutate(mean_age = mean_age_1/AVG_MONTH,
         year = as.numeric(str_sub(short_cite, -5, -2)))   %>%
  filter(mean_age < 150) # exclude MR population?
```

## Summary of coded data
```{r}
summary(ma_c)

count(ma_c, infant_type2) %>%
  kable(caption = "infant types")

count(ma_c, ME_trial_type) %>%
  kable(caption = "trial types")

N_d_calc <- length(ma_c$d_calc)

N_lab_groups <- length(unique(ma_c$lab_group))

N_papers <- length(unique(ma_c$study_ID))
```

There are `r N_d_calc` conditions.  There are `r N_papers` in the sample. There are `r N_lab_groups` lab groups in the sample (lab group is defined as the senior author (common across studies), or the last author). 

```{r}
ma_c %>%
  count(!is.na(mean_production_vocab), infant_type) %>%
  kable(caption = "production vocab")

ma_c %>%
  count(!is.na(mean_comprehension_vocab)) %>%
  kable(caption = "comprehension vocab")

```

## Forest plot
```{r}


```

## Fail-safe-N
```{r, fail_safe_N}
CRIT_ES_VALUE <- .01 # must be > 0 

fsn <- get_fail_safe_N("mutex", ma_c, CRIT_ES_VALUE)
kable(fsn)
```

## Funnel plot
```{r, funnel_plot}

CRIT_95 <- 1.96 

funnel.es.data <- ma_c %>%
        mutate(se = sqrt(d_var_calc), 
         es = d_calc, 
         center = mean(d_calc), 
         lower_lim = max(se) + .05 * max(se))


# separate df for 95 CI funnel shape
funnel95.data.wide <- funnel.es.data %>%
                select(center, lower_lim) %>%
                summarise(x1 = (center-lower_lim * CRIT_95)[1], 
                          x2 = center[1],
                          x3 = center[1] + lower_lim[1] * CRIT_95,
                          y1 = -lower_lim[1],
                          y2 =  0, 
                          y3 = -lower_lim[1]) 

funnel95.data.x <- funnel95.data.wide  %>%
                  select(dplyr::contains("x")) %>%
                  gather("coordx", "x", 1:3) %>%
                  arrange(coordx) %>%
                  select(-coordx)

funnel95.data.y <- funnel95.data.wide  %>%
                  select(dplyr::contains("y")) %>%
                  gather("coordy", "y", 1:3) %>%
                  arrange(coordy) %>%
                  select(-coordy)

funnel95.data <- bind_cols(funnel95.data.x, funnel95.data.y)

ggplot(funnel.es.data, aes(x = d_calc, y = -se)) +
  xlab("Effect Size")  +
  ylab("Standard Error\n")  +
  scale_colour_solarized(name = "") +
  geom_polygon(aes(x = x, y = y), 
               data = funnel95.data,
               fill = "white") +
  geom_vline(aes(xintercept=x2), 
             linetype = "dashed", color = "red", size = .8, data = funnel95.data.wide) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey44",  
             size = .8) +
  scale_y_continuous(labels = function(x){abs(x)}) +
  geom_point(size = .5) +
  theme(panel.grid.major = element_line(colour = "grey", size = 0.2),
        panel.grid.minor = element_line(colour = "grey", size = 0.5),
        strip.text.x = element_text(size = 9),
        strip.background = element_rect(fill="grey")) 
```

With age and response mode and trial type moderators
```{r, funnel_plot2}

mod <- rma(d_calc ~ mean_age + response_mode + ME_trial_type, d_var_calc, data = ma_c)

resids <- rstandard(mod)

funnel.es.data <- resids %>%
        as.data.frame() %>%
        mutate(center = mean(z),
                lower_lim = max(se) + .05 * max(se))


# separate df for 95 CI funnel shape
funnel95.data.wide <- funnel.es.data %>%
                select(center, lower_lim) %>%
                summarise(x1 = (center-lower_lim * CRIT_95)[1], 
                          x2 = center[1],
                          x3 = center[1] + lower_lim[1] * CRIT_95,
                          y1 = -lower_lim[1],
                          y2 =  0, 
                          y3 = -lower_lim[1]) 

funnel95.data.x <- funnel95.data.wide  %>%
                  select(dplyr::contains("x")) %>%
                  gather("coordx", "x", 1:3) %>%
                  arrange(coordx) %>%
                  select(-coordx)

funnel95.data.y <- funnel95.data.wide  %>%
                  select(dplyr::contains("y")) %>%
                  gather("coordy", "y", 1:3) %>%
                  arrange(coordy) %>%
                  select(-coordy)

funnel95.data <- bind_cols(funnel95.data.x, funnel95.data.y)

ggplot(funnel.es.data, aes(x = z, y = -se)) +
  xlab("Standardized Effect Size Residuals")  +
  ylab("Standard Error\n")  +
  scale_colour_solarized(name = "") +
  geom_polygon(aes(x = x, y = y), 
               data = funnel95.data,
               fill = "white") +
  geom_vline(aes(xintercept=x2), 
             linetype = "dashed", color = "red", size = .8, data = funnel95.data.wide) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey44",  
             size = .8) +
  scale_y_continuous(labels = function(x){abs(x)}) +
  geom_point(size = .5) +
  theme(panel.grid.major = element_line(colour = "grey", size = 0.2),
        panel.grid.minor = element_line(colour = "grey", size = 0.5),
        strip.text.x = element_text(size = 9),
        strip.background = element_rect(fill="grey")) 
```

Eggers test
```{r}
eggers <- eggers_tests(ma_c %>% mutate(short_name = "mutex")) 

kable(eggers)
  #eggers_test <- regtest(mod)
# this doesn't change when include age as moderator

```

Evidence for skew. Lots of heterogenity.


## P-curve
```{r get_pcurves}
ALPHA <- .05
P_INCREMENT <- .01 
ma_c_for_pcurve = ma_c %>% 
  mutate(r = NA, n_2 = NA, 
         participant_design = "within_one", 
         dataset = "mutex", r_calc = NA)
pc.data <- get_all_pc_data(ma_c_for_pcurve, ALPHA, P_INCREMENT, transform = TRUE) 

p.source <- pc.data %>%
  select(f.transform, f.value, dataset, study_ID, p_round) %>%
  group_by(dataset) %>%
  summarise(n.total = n(),
            n.transform = length(which(!is.na(f.transform))),
            sig.p = length(which(p_round < ALPHA))) %>%  
  mutate(stat_only = ifelse(n.total > n.transform, 1, 0),
         prop.ts = 1-n.transform/n.total,
         prop.ts.string = formatC(round(prop.ts, 2), 
                                format='f', digits = 2)) %>%
  arrange(-stat_only) %>%
  as.data.frame()

ci.data <- get_all_CIS_multi(pc.data, ALPHA, P_INCREMENT)

pc_plot_data <- get_p_curve_df(pc.data, ALPHA, P_INCREMENT)

ggplot(pc_plot_data) + 
  geom_ribbon(aes(ymin = ci.lower, ymax = ci.upper, x = p), 
              fill = "grey87", data = ci.data) +
  geom_line(size = 1, aes(x = p, y = value, linetype = measure,
                          color = measure)) +
  scale_colour_manual(name = "", values = c("red", "green", "blue"), 
                      labels=c("Null of no effect", 
                               "Null of 33% power", "Observed")) +
  scale_linetype_manual(values = c("dashed", "dashed", "solid"), 
                        guide = FALSE)  +
  ylab("Proportion p-values\n") +
  xlab("p-value") +
  #geom_text(aes(label = paste(sig.p, "sig. ps /", 
  #                            n.total, "conditions\nprop. test stat. = ", prop.ts.string),
  #              x = .021, y = .8), data = p.source, 
  #          colour = "black", size = 2, hjust = 0) +
  theme_bw() + 
  theme(legend.position = "top",
        legend.key = element_blank(),
        legend.background = element_rect(fill = "transparent"),
        strip.text.x = element_text(size = 9),
        axis.title = element_text(colour = "black", size = 12),
        panel.margin = unit(.65, "lines"),
        strip.background = element_rect(fill = "grey"))

```

Stouffer test
```{r}
stouffer.data <- stouffer_test(pc.data, ALPHA) %>%
    filter(pp.measure == "ppr.full")  
  kable(stouffer.data)
```

Strong evidence for left skew (no phacking).

## MA models
### Simple (no moderators)
```{r}
m1 <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)
summary(m1)
```

### ME_trial type
```{r}
m1a <- rma.mv(d_calc ~ ME_trial_type + mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)
summary(m1a)

m1a <- rma.mv(d_calc ~ ME_trial_type, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)
summary(m1a)
```

### Age
```{r}
m2 <- rma.mv(d_calc ~ mean_age + ME_trial_type, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)
summary(m2)
```

Age is reliable, controling for ME_trial_type

### Vocab

(we don't have production scores for any NN trials)
```{r}
m3a <- rma.mv(d_calc ~ mean_production_vocab , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)
summary(m3a)
```
Vocab is reliable

### Age + Vocab

#### Plots

Correlation between age and vocab:

```{r}
ma_c_av_complete <- ma_c %>%
  filter(!is.na(mean_production_vocab), !is.na(mean_age))

cor.test(ma_c_av_complete$mean_age, ma_c_av_complete$mean_production_vocab) %>%
  tidy() %>%
  kable()

ggplot(ma_c_av_complete, aes(x = mean_age, y = mean_production_vocab)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw()

cor.test(ma_c$mean_comprehension_vocab, ma_c$mean_production_vocab, na.rm = T)
```

Age and vocab are weakly correlated, not quite significant. Note the heterskadastisky!

Age and vocab vs. effect size

```{r}
ggplot(ma_c_av_complete, aes(x = mean_age, y = d_calc)) +
  geom_point(aes(color = infant_type)) +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  theme_bw()

ggplot(ma_c_av_complete, aes(x = mean_production_vocab, y = d_calc)) +
  geom_point(aes(color = infant_type)) +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  theme_bw()
```

Typical only

```{r}

ggplot(ma_c_av_complete %>% filter(infant_type == "typical"), 
       aes(x = mean_age, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  theme_bw()

ggplot(ma_c_av_complete %>% filter(infant_type == "typical"), 
       aes(x = mean_production_vocab, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  theme_bw()
```

#### Models
```{r}
m2_complete <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c_av_complete)
summary(m2_complete)

m3a_complete <- rma.mv(d_calc ~ mean_production_vocab , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c_av_complete)
summary(m3a_complete)

m4a <- rma.mv(d_calc ~ mean_age + mean_production_vocab, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c_av_complete)
summary(m4a)
```

Typical only:

```{r}

m4b <- rma.mv(d_calc ~ mean_age + mean_production_vocab, V = d_var_calc,
                            random = ~ 1 | short_cite, data = filter(ma_c_av_complete, infant_type == "typical"))
summary(m4b)
```

With set of conditions with complete production and age, age is not a reliable predictor, vocab is. In model with both, vocab is reliable. But for subset of typical participants, age but not vocab is predictive.


## Misc MA summary stats (for typical only)


Some evidence for a relationship between effect size and sample size: smaller ES, bigger ns (residualizing out age and method)

### Sample size and effect size
```{r}
d_resid <- lm(d_calc ~ mean_age * response_mode, 
              data = filter(ma_c, infant_type == "typical"))

ma_cd <- ma_c %>%
    filter(infant_type == "typical")  %>%
    add_residuals(d_resid)

# n_1 vs. age and method residulaed effect size 
ma_cd %>%
  filter(infant_type == "typical") %>%
  ggplot(aes(x = n_1,
             y = resid)) +
  geom_point() +
  geom_smooth(method = "lm")
```

### ME trial type

Controling for age, huge effect of ME_trial_type
```{r}
ma_cd %>%
  filter(infant_type == "typical") %>%
  group_by(ME_trial_type) %>%
  multi_boot_standard(col = "d_calc") %>%
  ggplot(aes(x = ME_trial_type, y = mean, 
             fill = ME_trial_type)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper))

ma_cd %>%
  filter(infant_type == "typical") %>%
  group_by(ME_trial_type) %>%
  multi_boot_standard(col = "resid") %>%
  ggplot(aes(x = ME_trial_type, y = mean, 
             fill = ME_trial_type)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper))
```

### Stimulus type

No effect

```{r}
ma_cd %>%
  filter(infant_type == "typical") %>%
  group_by(object_stimulus) %>%
  multi_boot_standard(col = "d_calc") %>%
  ggplot(aes(x = object_stimulus, y = mean, 
             fill = object_stimulus)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper))

ma_cd %>%
  filter(infant_type == "typical") %>%
  group_by(object_stimulus) %>%
  multi_boot_standard(col = "resid") %>%
  ggplot(aes(x = object_stimulus, y = mean, 
             fill = object_stimulus)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper))
```

### Lab group

Not interpretable (small sample sizes)

```{r}
# lab group
ma_cd %>%
  filter(infant_type == "typical") %>%
  group_by(study_ID, lab_group) %>%
  summarize(resid = mean(resid)) %>%
  group_by(lab_group) %>%
  summarize(mean = mean(resid)) %>%
  ggplot(aes(x = reorder(lab_group, mean), 
             y = mean, fill = lab_group)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(legend.position = "none")
```

### Time
Effect gets bigger over time, residulaizing out method and age
```{r}
# year vs. age and method residulaed effect size

ma_cd %>%
  filter(infant_type == "typical") %>%
  ggplot(aes(x = year,
             y = resid)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Mega developmental plot

```{r, fig.height = 8, fig.pos = 'T!'}
ma_plotting <- ma_c %>%
  mutate(es_type = ifelse(infant_type2 != "typical",
                          "Non-Typical Populations",
                          ifelse(ME_trial_type == "NN", 
                                 "Novel-Novel", "Familiar-Novel")),
         es_type = ifelse(es_type == "Non-Typical Populations" &  infant_type2 %in% c("bilingual", "trilingual"), "Multi-Lingual", 
                          ifelse(es_type == "Non-Typical Populations", "Non-Typical Populations", es_type)),
        es_type = fct_relevel(es_type, "Familiar-Novel", "Novel-Novel"),

         infant_type2_label = ifelse(infant_type2 == "typical",
                                     "", as.character(infant_type2)),
         infant_type2_label = fct_recode(infant_type2_label, 
                                         LT = "late_talkers", 
                                         DHH = "deaf/hard-of-hearing", 
                                         B = "bilingual", 
                                         `T` = "trilingual",
                                         MR = "youth with mental retardation"),
         d_var_calc2 = ifelse(es_type == "Non-Typical Populations", 
                                d_var_calc, 0),
         d_calc2 = ifelse(es_type == "Non-Typical Populations", 
                                d_calc, 0),
         d_var_calc2 = d_var_calc,
         d_calc2 = d_calc,
         effects.cil = d_calc2 -
               qnorm(.05 / 2, lower.tail = FALSE) * sqrt(d_var_calc2),
         effects.cih = d_calc2 +
               qnorm(.05 / 2, lower.tail = FALSE) * sqrt(d_var_calc2)) %>%
        filter(mean_age < 75 | es_type == "Non-Typical Populations")

NF_only <- ma_plotting %>%
  filter(infant_type2 == "typical",
         ME_trial_type == "FN") %>%
  select(d_calc, mean_age)

all_FN <- mutate(NF_only, 
                 es_type = "Familiar-Novel", 
                 line_group = 1) %>%
          bind_rows(mutate(NF_only, 
                           es_type = "Novel-Novel",
                           line_group = 2)) %>%
          bind_rows(mutate(NF_only, 
                           es_type = "Non-Typical Populations",
                           line_group = 2)) %>%
          bind_rows(mutate(NF_only, 
                           es_type = "Multi-Lingual",
                           line_group = 2)) %>%
          mutate(es_type = fct_relevel(es_type, "Familiar-Novel", "Novel-Novel"))

NN_NT_only <- ma_plotting %>%
  mutate(d_calc = ifelse(infant_type2 == "typical" & 
                            ME_trial_type  == "FN", NA, d_calc),
         mean_age = ifelse(infant_type2 == "typical" & 
                            ME_trial_type  == "FN", NA, mean_age),
         es_type = fct_relevel(es_type, "Familiar-Novel", "Novel-Novel")) %>%
  select(study_ID, d_calc, mean_age, infant_type2, ME_trial_type, es_type) 

ma_plotting %>%
  ggplot(aes(x = mean_age, y = d_calc)) +
    facet_wrap( ~ es_type, scale = "free_x", 2) +
    geom_hline(aes(yintercept = 0)) +
    geom_linerange(aes(ymin = effects.cil, ymax = effects.cih), 
                   alpha = .5, size = .3) +
    geom_point(aes(size = n_1, shape = ME_trial_type), alpha = .5) +
    geom_smooth(aes(linetype = as.factor(line_group)), 
                method = "lm", formula = y ~ log(x), color = "#268bd2",
                data = all_FN, se = FALSE, size = 1.1) +
    geom_smooth(aes(y = d_calc, x = mean_age, color = es_type), 
                method = "lm", formula = y ~ log(x), 
                data = NN_NT_only, se = FALSE, size = 1.1) +
    scale_color_manual(values= c("#b58900", "#d33682", "#6c71c4"), guide = FALSE) +
    ggrepel::geom_text_repel(aes(label = infant_type2_label), box.padding = .5) +
    scale_shape_discrete(name = "Trial Type",
                         labels = c("Familiar-Novel", "Novel-Novel")) +
    scale_size_continuous(name="Sample size") +
    guides(linetype = FALSE,
           shape = guide_legend(override.aes = list(size = 4))) +
    xlab("Mean age (months)") +
    ylab("Effect size (d)") +
    ggtitle("Disambiguation Development from Meta-Analysis") +
   # theme_few()  +
    theme(legend.position = "bottom") 
```
