---
title: ME vocab analyses with experimental and MA data
author: Molly Lewis
subtitle: 
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: cerulean
    code_folding: hide
---

Load packages
```{r setup, message = FALSE}
library(tidyverse)
library(lubridate)
library(langcog)
library(skimr) #devtools::install_github("hadley/colformat") #devtools::install_github("ropenscilabs/skimr")
library(corrr)
library(knitr)
library(feather)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, cache = F, tidy = F)

theme_set(theme_minimal())
```

constants
```{r}
AVG_MONTH <- 365.2425 / 12.0
```

# Experimental data
Read in participant-wise data.

```{r}
file_1 <- "../../data-flurry/summary-07-12-17.csv"
file_2 <- "../../data-flurry/summary-12-9-16.csv"
file_3 <- "../../data-flurry/summary-06-12-17.csv"
# file_3 <- "data-flurry/summary-2-7-17.csv" # this one is missing, but we may want it? (N doesn't match email - but maybe that's including excluded participants?)

mss <-  read_csv(file_1) %>%
        bind_rows(read_csv(file_2) %>% mutate(SubjectID = as.character(SubjectID))) %>%
        bind_rows(read_csv(file_3)) %>%
        rename(sub_id = SubjectID) %>%
        mutate_at(vars(sub_id), funs(as.factor))

NUM_PARTICIPANTS <-  nrow(mss)
```


```{r, include = F}
# Save demographics
demographics <- mss %>%
  distinct(subid) %>%
  select(sub_id, age, vocab_acc)

#write_csv(demographics, "demographics.csv")
```


```{r, include = F}
# Summarize data
skim(mss)


```

There are `r NUM_PARTICIPANTS` unique participants.


```{r}
mss_c <- filter(mss, !is.na(ME_acc)) %>%
  mutate(age_months = age  * 12) %>%
  select(sub_id, age_months, vocab_acc, ME_acc, everything())
```

```{r fig.height=2}
mss_c %>%
  gather("measure", "value", 2:4) %>%
  ggplot(aes(x = value, fill = measure)) +
  geom_histogram() +
  facet_wrap(~measure, scales = "free") +
  theme(legend.position = "none") 
```


## Developmental plots{.tabset}

### Age vs. Vocab
```{r}
ggplot(mss_c, aes(x = age_months, y = vocab_acc)) +
  geom_point() +
  geom_smooth(method = "lm",)
```

### Age vs. ME
```{r}
ggplot(mss_c, aes(x = age_months, y = ME_acc)) +
  geom_point() +
  geom_smooth(method = "lm",)
```

### Vocab vs. ME
```{r}
ggplot(mss_c, aes(x = vocab_acc, y = ME_acc)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Stats

### Correlations
```{r}
mss_c %>%
  select(age_months, vocab_acc, ME_acc)  %>%
  correlate() %>%
  shave() %>%
  kable()
```

### Partial Correlations
ME and vocab, controlling for age
```{r}
ppcor::pcor.test(mss_c$ME_acc, mss_c$vocab_acc, mss_c$age_months) %>%
  kable()
```

Age and vocab, controlling for ME
```{r}
ppcor::pcor.test(mss_c$age_months, mss_c$vocab_acc, mss_c$ME_acc) %>%
  kable()
```

### GLMM model
```{r}

```

# MA data

Read in ME meta-analysis data in Metalab
```{r}
ma_raw <- read_feather("../data/mutual_exclusivity_metalab") %>%
  select(1, 3, 6, 9, 11, 12, 18, 20, 49, 52, 53, 95, 96) %>%
  mutate_if(is.character, as.factor)
```


```{r, include = F}
#Summarize data
skim(ma_raw)
```

## Developmental plots{.tabset}
```{r}
ma_c <- ma_raw %>%
  mutate(mean_age = mean_age_1/AVG_MONTH)
```

### Age vs. Vocab
```{r}
ma_c %>%
  filter(!is.na(mean_production_vocab),
           mean_age < 36) %>%
  ggplot(aes(x = mean_age, y = mean_production_vocab)) +
  geom_point(aes(size = n_1)) +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  xlab("Mean age (months)") +
  ylab("Mean CDI productive vocabulary") +
  theme(legend.position = "none")
```


### Age vs. ME
```{r}
ma_c %>%
ggplot(aes(x = mean_age, y = d_calc)) +
  geom_point(aes(size = n_1)) +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  xlab("mean age (months)") +
  ylab("Estimated effect size (d)") +
  ggtitle("all MA data - age") +
  theme(legend.position = "none")
```

### Age vs. ME subsetted (<36 & with production CDI)
```{r}
ma_c %>%
  filter(!is.na(mean_production_vocab),
           mean_age < 36) %>%
ggplot(aes(x = mean_age, y = d_calc)) +
  geom_point(aes(size = n_1)) +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  xlab("Mean age (months)") +
  ylab("Estimated effect size (d)") +
  ggtitle("production MA data - age") +
  theme(legend.position = "none")
```

### Vocab vs. ME subsetted  (<36 & with production CDI)
```{r}
ma_c %>%
  filter(!is.na(mean_production_vocab),
           mean_age < 36) %>%
  ggplot(aes(x = mean_production_vocab, y = d_calc)) +
  geom_point(aes(size = n_1)) +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  xlab("Mean CDI productive vocabulary") +
  ylab("Estimated effect size (d)") +
  ggtitle("production MA data - vocab") +
  theme(legend.position = "none")
```

## Stats

### Correlations
```{r}
ma_c %>%
  filter(!is.na(mean_production_vocab)) %>%
         #mean_age < 36)  %>%
  select(mean_age, mean_production_vocab, d_calc)  %>%
  correlate() %>%
  shave() %>%
  kable()
```

### Partial Correlations
ME and vocab, controlling for age
```{r}
ma_sub <- ma_c %>%
  filter(!is.na(mean_production_vocab))

ppcor::pcor.test(ma_sub$d_calc, ma_sub$mean_production_vocab, ma_sub$mean_age) %>%
  kable()
```

Age and vocab, controlling for ME
```{r}
ppcor::pcor.test(ma_sub$mean_age, ma_sub$mean_production_vocab, ma_sub$d_calc)%>%
  kable()
```

### Meta-analytic models
```{r}
metafor::rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)

metafor::rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)

metafor::rma.mv(d_calc ~ mean_production_vocab, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)

metafor::rma.mv(d_calc ~ mean_production_vocab + mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_c)
```


# Experimental + MA

## Age
```{r}
exp_es_age<- read_csv("experimental_es_by_age.csv")

all_age_data <- ma_c %>%
  select(n_1, mean_age, d_calc) %>%
  rename(n = n_1, d = d_calc) %>%
  mutate(source = "MA") %>%
  bind_rows(exp_es_age %>% select(n, mean_age, d) %>%
              mutate(source = "exp"))

all_age_data %>%
ggplot(aes(x = mean_age, y = d, color = source)) +
  geom_point(aes(size = n)) +
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  xlab("mean age (months)") +
  ylab("Estimated effect size (d)") +
  ggtitle("Exp. and MA data - AGE")

m = lm(d ~ mean_age, all_age_data)
```


## Vocab
```{r}
exp_es_vocab <- read_csv("experimental_es_by_vocab.csv")

all_vocab_data <- ma_c %>%
  select(n_1, mean_production_vocab, d_calc) %>%
  rename(n = n_1, d = d_calc, 
         mean_vocab = mean_production_vocab) %>%
  mutate(source = "MA") %>%
  bind_rows(exp_es_vocab %>% select(n, mean_vocab, d) %>%
              mutate(source = "exp"))

all_vocab_data %>%
  ggplot(aes(x = mean_vocab, y = d, color = source)) +
  geom_point(aes(size = n)) +
  facet_wrap(~source, scales = "free_x")+
  geom_smooth(method = "lm", formula = y ~ log(x)) +
  xlab("Vocabulary") +
  ylab("Estimated effect size (d)") +
  ggtitle("Exp. and MA data - VOCAB") 

```


