
# Meta-analysis

```{r}
library(metafor)
ma_raw <- read_feather("../../MA/data/mutual_exclusivity") %>%
  select(c(1, 3, 6, 9, 12, 14, 15, 18, 20, 22:24, 26,
           29:30, 49, 51:53, 95:99, 100, 102:103)) %>%
  mutate_if(is.character, as.factor)

AVG_MONTH <- 30.43688
ma_c <- ma_raw %>%
  filter(!is.na(d_calc)) %>%
  mutate(mean_age = mean_age_1/AVG_MONTH,
         year = as.numeric(str_sub(short_cite, -5, -2)))  %>%
  filter(mean_age < 150) # exclude MR population?
```

## Methods


### Search strategy
We conducted a forward search based on citations of Markman and Wachtel (1988) in Google Scholar, and by using the keyword combination 'mutual exclusivity' in Google Scholar (September 2013; November 2017). Additional papers were identified through citations and by consulting experts in the field. We then narrowed our sample to the subset that used one of two paradigms: (a) the canonical experimental paradigm for testing disambiguation behavior (an experimenter says a novel word in the context of a familiar object and a novel object, and the child guesses the intended referent; "Familiar-Novel"), or (b) a paradigm that exposed children to an unambigous mapping of a novel label to a novel object, and then introduced a second novel object and asked children to identify the referent of a second novel label ("Novel-Novel"). For Familiar-Novel conditions, we included conditions that included more than one familiar object (e.g. Familiar-Familar-Novel). From these conditions, we restricted our sample to only those that satisfied the following criteria: (a) participants were children (less than 12 years of age)\footnote{This cutoff was arbitrary but allowed us to include conditions from older children in non-typically-developing populations.}, (b) referents were objects or pictures (not facts or object parts), (c) no incongruent cues (e.g. eye gaze at familiar object). All papers used either forced-choice pointing or eye-tracking methodology. All papers were peer-reviewed with the exception of two dissertations (Williams, 2009; Frank, I., 1999), but all  main results reported below remain the same when these papers are excluded. In total, we identified `r length(unique(ma_c$study_ID))` papers that satisfied our selection criteria, and had sufficient information to calculate an effect size.


### Coding
For each paper, we coded separately each relevant condition with each age group entered as a separate condition. For each condition, we coded the paper metadata (citation) as well as several potential moderator variables: mean age of infants, method (pointing or eyetracking), participant population type, estimates of vocabulary size from the Words and Gestures form of the MacArthur-Bates Communicative Development Inventory when available [MCDI; @fenson1994variability,@fenson2007macarthur], referent type (object or picture), and number of alternatives in the forced choice task. We coded participant population as one of three types that have tested in the literature, and have been argued to provide theoretical insight into the underlying mechanisms of the disambiguation effect: (a) typically-developing monolingual chilldren, (b) multilingual children (including both bilingual and trilingual children), and (c) non-typically developing children. Non-typically developing conditions included children with selective language imparement, language delays, hearing imparement, autism spectrum disorder, and down-syndrome.

In order to estimate effect size for each conditions, we coded several additional variables: sample size, proportion novel-object selections, baseline (e.g., .5 in a 2-AFC paradigm), and standard deviations for novel object selections, t-statistic, and Cohen's d. For several conditions, there was data were insufficient data reported in the main text to calculate an effect size (no means and standard deviations, t-statistics, or Cohen's ds), but we were able to esimtate the means and standard deviations though measurement of plots (N = `r count(ma_c, data_source) %>% filter(data_source == "figure") %>% select(n) %>% as.numeric()`), imputation from other data within the paper (N = `r count(ma_c, data_source) %>% filter(data_source == "paper - some imputation") %>% select(n) %>% as.numeric()`; see SI for details), or through contacting authors (N = `r count(ma_c, data_source) %>% filter(data_source == "paper/author") %>% select(n) %>% as.numeric()`). Our final sample included `r length(ma_c$d_calc)` effect sizes (N~typical-developing~ = `r count(ma_c, infant_type) %>% filter(infant_type == "typical") %>% select(n) %>% as.numeric()`; N~multilingual~ = `r count(ma_c, infant_type) %>% filter(infant_type == "multilingual") %>% select(n) %>% as.numeric()`; N~non-typically-developing~ = `r count(ma_c, infant_type) %>% filter(infant_type == "NT") %>% select(n) %>% as.numeric()`).

### Statistical approach
Effect sizes were computed by a script, compute_es.R, available in the Github repository. We calculated effect sizes from reported means and standard deviations where available, otherwise we relied on reported test-statistics (t or d). All analyses were conducted with the metafor package (Viechtbauer, 2010) using mixed-effect models with grouping by paper. \footnote{The exact model specification was as follows: $model <- metafor::rma.mv(yi = effect_size, V = effect_size_var, random = ~ 1 | paper, data = d$.} In models with moderators, moderators variables were included as additive fixed effects.

## Results

### Bias
We first conducted analyses to determine if there was bias present in the literature.  see metalab 


### Effect size estimates
```{r, overall_estimates}
## grand model (all effect sizes)
grand_model <- rma.mv(d_calc, V = d_var_calc,
                              random = ~ 1 | short_cite,
                              method = "REML",
                              data = ma_c)


grand_model_data <- data.frame(model_name = "grand",
                                estimate = grand_model$b[1],
                                estimate.cil = grand_model$ci.lb,
                                estimate.cih = grand_model$ci.ub,
                                es_type = "grand",
                                model_type = "overall") 

# NN only model
#nn_model <- rma.mv(d_calc, V = d_var_calc,
#                   random = ~ 1 | short_cite,
#                   method = "REML",
#                   data = filter(ma_c, ME_trial_type == "NN"))

#nn_model_data <- data.frame(model_name = "NN",
#                            estimate = nn_model$b[1],
#                             estimate.cil = nn_model$ci.lb,
#                             estimate.cih = nn_model$ci.ub,
#                             es_type = "sub",
#                             model_type = "sub")
# 
# # FN only model
# fn_model <- rma.mv(d_calc, V = d_var_calc,
#                    random = ~ 1 | short_cite,
#                    method = "REML",
#                    data = filter(ma_c, ME_trial_type == "FN"))
# 
# fn_model_data <- data.frame(model_name = "FN",
#                             estimate = fn_model$b[1],
#                             estimate.cil = fn_model$ci.lb,
#                             estimate.cih = fn_model$ci.ub,
#                             es_type = "sub",
#                             model_type = "sub")


# typical only model
typical_model <- rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | short_cite,
                      method = "REML",
                      data = filter(ma_c, infant_type == "typical"))

typical_model_data <- data.frame(model_name = "typical",
                                 estimate = typical_model$b[1],
                                 estimate.cil = typical_model$ci.lb,
                                 estimate.cih = typical_model$ci.ub,
                                 es_type = "sub",
                                 model_type = "sub")


# multi-lingual only model
ml_model <- rma.mv(d_calc, V = d_var_calc,
                        random = ~ 1 | short_cite,
                        method = "REML",
                        data = filter(ma_c, infant_type == "multilingual"))


ml_model_data <- data.frame(model_name = "multilingual",
                                 estimate = ml_model$b[1],
                                 estimate.cil = ml_model$ci.lb,
                                 estimate.cih = ml_model$ci.ub,
                                 es_type = "sub",
                            model_type = "sub")


# non-typical only model
nt_model <- rma.mv(d_calc, V = d_var_calc,
                   random = ~ 1 | short_cite,
                   method = "REML",
                   data = filter(ma_c, infant_type == "NT"))

nt_model_data <- data.frame(model_name = "NT",
                                 estimate = nt_model$b[1],
                                 estimate.cil = nt_model$ci.lb,
                                 estimate.cih = nt_model$ci.ub,
                                 es_type = "sub",
                                 model_type = "sub")
```

```{r, forest_prep}
ns <- bind_rows(list(count(ma_c, infant_type) %>% rename(model_name = infant_type)), 
                count(ma_c, ME_trial_type) %>% rename(model_name = ME_trial_type)) %>%
                add_row(model_name = "grand", n = mean(.$n))

all_overall_estimates <- bind_rows(list(grand_model_data, 
                                        typical_model_data, 
                                        ml_model_data, 
                                        nt_model_data
                                        #fn_model_data,
                                        #nn_model_data
                                        )) %>%
                          left_join(ns) %>%
                          mutate(es_string = paste0(round(estimate,2),
                                                   " [", 
                                                    round(estimate.cil,2),
                                                    ", ",
                                                    round(estimate.cih,2),
                                                    "]")) %>%
                          add_row(model_name = "", model_type = "sub") %>%
                          mutate(model_name = fct_relevel(model_name, 
                                                     "typical", "multilingual",
                                                     "NT",  "", "grand"),
                                 model_name = fct_rev(model_name),
                                 model_type = fct_rev(model_type))

 breaks <- seq(-.25, 2.5, .25)
 labels <- as.character(breaks)
 labels[!(breaks%%1==0)] <- ''
 tick.sizes <- rep(.5, length(breaks))
 tick.sizes[(breaks%%1==0)] <- 1
```


To estimate the overall effect size, we fit a mixed effect model for the full sample of conditions. Effect size estimates or presented in Figure 1. The overall effect size estimate reliably differed from zero (d = `r filter(all_overall_estimates, model_name == "grand") %>% select(es_string) %>% as.character()`; see Appendix for by-condition forest plots). We also fit additional models for sub-populations in our sample (d~typically-developing~ = `r filter(all_overall_estimates, model_name == "typical") %>% select(es_string) %>% as.character()`; d~multilingual~ = `r filter(all_overall_estimates, model_name == "typical") %>% select(es_string) %>% as.character()`; d~non-typically-developing~ = `r filter(all_overall_estimates, model_name == "NT") %>% select(es_string) %>% as.character()`). In the next set of analyses, we ask whether our moderator variables predict variance in these overall effect size estimates. 

#### Trial type, referent type, and number of alternatives
```{r}
# trial type
trial_type_model <- rma.mv(d_calc ~ ME_trial_type, V = d_var_calc,
                      random = ~ 1 | short_cite,
                      method = "REML",
                      data = ma_c)

trial_type_es_string =  paste0(round(trial_type_model$b[2],2),
                                                   "; Z = ",
                                                  round(trial_type_model$zval[2],2),
                                                  "; p = <.001 ")
                                                   # round(trial_type_model$pval[2],2)

# referent type
#referent_type_model <- rma.mv(d_calc ~ object_stimulus, V = d_var_calc,
#                      random = ~ 1 | short_cite,
#                      method = "REML",
#                      data = ma_c)

#referent_type_es_string =  paste0(round(referent_type_model$b[2],2),
#                                                   "; Z = ",
##                                                  round(referent_type_model$zval[2],2),
#                                                  "; p = ",
#                                  round(trial_type_model$pval[2],2))
# paper is reliable when you don't control for age


# N_AFC type
NAFC_model <- rma.mv(d_calc ~ N_AFC + mean_age, V = d_var_calc,
                      random = ~ 1 | short_cite,
                      method = "REML",
                      data = ma_c)

NAFC_model_es_string =  paste0(round(NAFC_model$b[2],2),
                                                  "; Z = ",
                                                  round(NAFC_model$zval[2],2),
                                                  "; p = ",
                                  round(NAFC_model$pval[2],2))


```
Here we examined the influnce of three methodological varirables -- trial type, referent type and number of alternatives -- on effect size. Trial type was a signifcant predictor of effect size, with Familiar-Novel conditions leading to overall larger effect sizes, compared to Novel-Novel conditions ($\beta$ = `r trial_type_es_string`). Referent type (object vs. picture; ) and number of alternatives () were not reliable predictors of effect size.

#### Age 
We next examine developmental change in the magnitude of the disambiguation effect. See Table 1.

#### Vocabulary 

```{r, fig.cap = "Mixed-effect effect size estimates for all conditions (red) and each of the three sub-populations in our sample. Ranges are 95% confidence intervals. The size of the point for the sub-populations corresponds to sample size."}
p1 <- ggplot(all_overall_estimates, aes(x = model_name,
                                  y = estimate, 
                                  color = model_type)) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +
  geom_point(aes(size = n, 
                 shape = model_type)) +
  geom_linerange(aes(ymin = estimate.cil, 
                     ymax = estimate.cih)) +
  geom_text(aes(label = es_string, x = model_name, y = 3.25), 
            size = 3.5) +
  coord_flip() 

p1 <- p1 + scale_shape_manual(values = c(16, 15)) +
  scale_color_manual(values = c("#000000", '#FF0000')) +
  scale_size_continuous(guide = FALSE) +
  scale_y_continuous(breaks = breaks, 
                     labels = labels,
                     limits = c(-.25, 3.75),
                     name = "Effect Size") +
  scale_x_discrete(labels = c("NT" = "Non-Typically-Developing populations", 
                              "grand" = "Overall estimate",
                              "typical" = "Typically-Developing populations",
                              #"FN" = "Familiar-Novel trial type", 
                              #"NN" = "Novel-Novel trial type",
                              "multilingual" = "Multilingual populations"),
                   name = "") + 
  ggtitle("Mixed-effect estimates of overall effect size") 

p1 <- p1 + 
  theme_bw() +
  theme(axis.line.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "none",
        axis.ticks.x = element_line(size = tick.sizes),
        axis.ticks.y = element_line(size = 0),
        axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12, 
                                   colour = c('red', rep('black', 4)),
                                   face = c("bold", rep("plain", 4))),
        plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 14))
p1
```

```{r, moderator_table}
### MODERATED ESTIMATES
grand_modelm <- rma.mv(d_calc ~ ME_trial_type + mean_age, V = d_var_calc,
                      random = ~ 1 | short_cite,
                      method = "REML",
                      data = ma_c)
grand_model_datam <- data.frame(estimate = as.vector(grand_modelm$b[,1]),
                                estimate.cil = as.vector(grand_modelm$ci.lb),
                                estimate.cih = as.vector(grand_modelm$ci.ub),
                                zval =  as.vector(grand_modelm$zval),
                                pval =  as.vector(grand_modelm$pval),
                                effect_name = rownames(grand_modelm$b)) %>%
                        mutate(model_name = "Grand estimate")

# typical
typical_modelm <- rma.mv(d_calc ~ ME_trial_type + mean_age, V = d_var_calc,
                        random = ~ 1 | short_cite,
                        method = "REML",
                        data = filter(ma_c, infant_type == "typical"))

typical_model_datam <- data.frame(estimate = as.vector(typical_modelm$b[,1]),
                                estimate.cil = as.vector(typical_modelm$ci.lb),
                                estimate.cih = as.vector(typical_modelm$ci.ub),
                                zval =  as.vector(typical_modelm$zval),
                                pval =  as.vector(typical_modelm$pval),
                                effect_name = rownames(typical_modelm$b)) %>%
  mutate(model_name = "Typical populations")


# multi-lingual only model
ml_modelm <- rma.mv(d_calc ~ ME_trial_type + mean_age, V = d_var_calc,
                   random = ~ 1 | short_cite,
                   method = "REML",
                   data = filter(ma_c, infant_type == "multilingual"))

ml_model_datam <- data.frame(estimate = as.vector(ml_modelm$b[,1]),
                                  estimate.cil = as.vector(ml_modelm$ci.lb),
                                  estimate.cih = as.vector(ml_modelm$ci.ub),
                                  zval =  as.vector(ml_modelm$zval),
                                  pval =  as.vector(ml_modelm$pval),
                                  effect_name = rownames(ml_modelm$b)) %>%
  mutate(model_name = "Multilingual populations")

# non-typical only model
nt_modelm <- rma.mv(d_calc ~ ME_trial_type + mean_age, V = d_var_calc,
                   random = ~ 1 | short_cite,
                   method = "REML",
                   data = filter(ma_c, infant_type == "NT"))


nt_model_datam <- data.frame(estimate = as.vector(nt_modelm$b[,1]),
                             estimate.cil = as.vector(nt_modelm$ci.lb),
                             estimate.cih = as.vector(nt_modelm$ci.ub),
                             zval =  as.vector(nt_modelm$zval),
                             pval =  as.vector(nt_modelm$pval),
                             effect_name = rownames(nt_modelm$b)) %>%
  mutate(model_name = "Non-typically developing populations")


all_moderated_estimates <- bind_rows(list(grand_model_datam, 
                                          typical_model_datam, 
                                          ml_model_datam, 
                                          nt_model_datam)) %>%
  mutate(beta = paste0(round(estimate,2),
                            " [", 
                              round(estimate.cil,2),
                             ", ",
                             round(estimate.cih,2),
                             "]"),
         pval = round(pval,2),
         pval = ifelse(pval <.001, "<.001", pval),
         zval = round(zval, 2))  %>%
  select(model_name, effect_name, beta, zval, pval) %>%
  rename(Model = "model_name", `Fixed effect` = "effect_name", 
         `z-value` = "zval", `p-value` = "pval") 

kable(all_moderated_estimates, format = "latex", booktabs = TRUE) %>%
  kable_styling(font_size = 7)
```


```{r, fig.height = 8, fig.pos = 't!', fig.cap = "Developmental plots for each moderator. Ranges correspond to 95% confidence intervals. Model fits are log-linear."}
ma_plotting <- ma_c %>%
  mutate(es_type = ifelse(infant_type2 != "typical",
                          "Non-Typical Populations",
                          ifelse(ME_trial_type == "NN", 
                                 "Novel-Novel", "Familiar-Novel")),
         es_type = ifelse(es_type == "Non-Typical Populations" &  infant_type2 %in% c("bilingual", "trilingual"), "Multi-Lingual", 
                          ifelse(es_type == "Non-Typical Populations", "Non-Typical Populations", es_type)),
        es_type = fct_relevel(es_type, "Familiar-Novel", "Novel-Novel"),

         infant_type2_label = ifelse(infant_type2 == "typical",
                                     "", as.character(infant_type2)),
         infant_type2_label = fct_recode(infant_type2_label, 
                                         LT = "late_talkers", 
                                         DHH = "deaf/hard-of-hearing", 
                                         B = "bilingual", 
                                         `T` = "trilingual",
                                         MR = "youth with mental retardation"),
         d_var_calc2 = ifelse(es_type == "Non-Typical Populations", 
                                d_var_calc, 0),
         d_calc2 = ifelse(es_type == "Non-Typical Populations", 
                                d_calc, 0),
         d_var_calc2 = d_var_calc,
         d_calc2 = d_calc,
         effects.cil = d_calc2 -
               qnorm(.05 / 2, lower.tail = FALSE) * sqrt(d_var_calc2),
         effects.cih = d_calc2 +
               qnorm(.05 / 2, lower.tail = FALSE) * sqrt(d_var_calc2)) %>%
        filter(mean_age < 75 | es_type == "Non-Typical Populations")

NF_only <- ma_plotting %>%
  filter(infant_type2 == "typical",
         ME_trial_type == "FN") %>%
  select(d_calc, mean_age)

all_FN <- mutate(NF_only, 
                 es_type = "Familiar-Novel", 
                 line_group = 1) %>%
          bind_rows(mutate(NF_only, 
                           es_type = "Novel-Novel",
                           line_group = 2)) %>%
          bind_rows(mutate(NF_only, 
                           es_type = "Non-Typical Populations",
                           line_group = 2)) %>%
          bind_rows(mutate(NF_only, 
                           es_type = "Multi-Lingual",
                           line_group = 2)) %>%
          mutate(es_type = fct_relevel(es_type, "Familiar-Novel", "Novel-Novel"))

NN_NT_only <- ma_plotting %>%
  mutate(d_calc = ifelse(infant_type2 == "typical" & 
                            ME_trial_type  == "FN", NA, d_calc),
         mean_age = ifelse(infant_type2 == "typical" & 
                            ME_trial_type  == "FN", NA, mean_age),
         es_type = fct_relevel(es_type, "Familiar-Novel", "Novel-Novel")) %>%
  select(study_ID, d_calc, mean_age, infant_type2, ME_trial_type, es_type) 

ma_plotting %>%
  ggplot(aes(x = mean_age, y = d_calc)) +
    facet_wrap( ~ es_type, scale = "free_x", 2) +
    geom_hline(aes(yintercept = 0)) +
    geom_linerange(aes(ymin = effects.cil, ymax = effects.cih), 
                   alpha = .5, size = .3) +
    geom_point(aes(size = n_1, shape = ME_trial_type), alpha = .5) +
    geom_smooth(aes(linetype = as.factor(line_group)), 
                method = "lm", formula = y ~ log(x), color = "#268bd2",
                data = all_FN, se = FALSE, size = 1.1) +
    geom_smooth(aes(y = d_calc, x = mean_age, color = es_type), 
                method = "lm", formula = y ~ log(x), 
                data = NN_NT_only, se = FALSE, size = 1.1) +
    scale_color_manual(values= c("#b58900", "#d33682", "#6c71c4"), guide = FALSE) +
    ggrepel::geom_text_repel(aes(label = infant_type2_label), box.padding = .5) +
    scale_shape_discrete(name = "Trial Type",
                         labels = c("Familiar-Novel", "Novel-Novel")) +
    scale_size_continuous(name="Sample size") +
    guides(linetype = FALSE,
           shape = guide_legend(override.aes = list(size = 4))) +
    xlab("Mean age (months)") +
    ylab("Effect size (d)") +
    ggtitle("Disambiguation Development from Meta-Analysis") +
    theme_few()  +
    theme(legend.position = "bottom") 
```


## Bilingualism


## Autism Spectrum Disorders



```{r, eval = F}
funnel.es.data <- synthesis_all_data %>%
  mutate(dataset = fct_relevel(dataset, 
                               "Infant directed speech preference","Phonotactic learning", "Vowel discrimination (native)", 
                               "Vowel discrimination (non-native)","Statistical sound category learning", "Word segmentation",
                               "Mutual exclusivity", "Sound symbolism", "Label advantage in concept learning","Online word recognition",
                               "Gaze following",  "Pointing and vocabulary"),
         dataset = fct_recode(dataset,
                              "IDS preference" = "Infant directed speech preference",
                              "Statistical sound learning" = "Statistical sound category learning", 
                              "Concept-label advantage" = "Label advantage in concept learning",
                              "Vowel discrimination\n(native)" = "Vowel discrimination (native)",
                              "Vowel discrimination\n(non-native)" = "Vowel discrimination (non-native)")) %>%
  group_by(dataset) %>%
  mutate(se = sqrt(d_var_calc), 
         es = d_calc, 
         center = mean(d_calc), 
         lower_lim = max(se) + .05 * max(se))


# separate df for 95 CI funnel shape
funnel95.data.wide <- funnel.es.data %>%
  select(center, lower_lim, dataset) %>%
  group_by(dataset) %>%
  summarise(x1 = (center-lower_lim * CRIT_95)[1], 
            x2 = center[1],
            x3 = center[1] + lower_lim[1] * CRIT_95,
            y1 = -lower_lim[1],
            y2 =  0, 
            y3 = -lower_lim[1]) 

funnel95.data.x <- funnel95.data.wide  %>%
  select(dataset,  dplyr::contains("x")) %>%
  gather("coordx", "x", 2:4) %>%
  arrange(dataset, coordx) %>%
  select(-coordx)

funnel95.data.y <- funnel95.data.wide  %>%
  select(dataset, dplyr::contains("y")) %>%
  gather("coordy", "y", 2:4) %>%
  arrange(dataset, coordy) %>%
  select(-coordy)

funnel95.data <- bind_cols(funnel95.data.x, funnel95.data.y)

ggplot(funnel.es.data, aes(x = es, y = -se)) +
  facet_wrap(~dataset, scales = "free") +
  xlab("Effect Size")  +
  ylab("Standard Error\n")  +
  scale_colour_solarized(name = "") +
  geom_polygon(aes(x = x, y = y), 
               data = funnel95.data,
               fill = "white") +
  geom_vline(aes(xintercept=x2), 
             linetype = "dashed", color = "red", size = .8, data = funnel95.data.wide) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey44",  size = .8) +
  scale_y_continuous(labels = function(x){abs(x)}) +
  geom_point(size = .5) +
  theme(panel.grid.major = element_line(colour = "grey", size = 0.2),
        panel.grid.minor = element_line(colour = "grey", size = 0.5),
        strip.text.x = element_text(size = 9),
        strip.background = element_rect(fill="grey")) 
```

```{r, eval = F}
# MA STUFF TO DO:
- get proportion double checked by joan
- check sub sample
- check alvaros ones
- how deal with pointing + eyetracking one
- check eyetracking vs behavioral coding
- check for duplicates
- check paper vs. objects coding
```
