---
title             : "The role of experience in disambiguation during early word learning"
shorttitle        : "Disambiguation during early word learning"

author: 
  - name          : "Molly Lewis"
    affiliation   : "1, 6"
    corresponding : no    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Veronica Cristiano"
    affiliation   : "2"
  - name          : "Brenden Lake"
    affiliation   : "3"
  - name          : "Tammy Kwan"
    affiliation   : "4"
  - name          : "Michael C. Frank"
    affiliation   : "5"
  
affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "Gallaudet University"
  - id            : "3"
    institution   : "New York University"
  - id            : "4"
    institution   : "Cognitive Toybox, Inc."
  - id            : "5"
    institution   : "Stanford University"
  - id            : "6"
    institution   : "University of Wisconsin-Madison"

author_note: |
  Data from Experiment 2 were previously presented in the Proceedings of the Cognitive Science Society Conference in Lewis & Frank (2013). 
    $^*$To whom correspondence should be addressed. E-mail: mollylewis@uchicago.edu


abstract: |
  Young children tend to map novel words to novel objects even in the presence of familiar competitors, a finding that has been dubbed the “disambiguation” effect. This phenomenon is important because it could provide a strong constraint for children in learning new words. But, although the effect is highly robust and widely studied, the cognitive mechanisms underlying  it remain unclear. Existing theoretical accounts include a proposal for initial constraints on children’s lexicons (e.g. a principle of mutual exclusivity), situation-specific pragmatic inferences, probabilistic accounts, and overhypothesis account. In the current paper, we have two goals: synthesize the existing body of literature and directly examine the causal role of experience on the  effect. We present a synthesis of existing evidence through a meta-analysis of the existing literature, followed by two experiments that examine the relationship between vocabulary development and the disambiguation  effect. We conclude by summarizing the empirical landscape, and suggest that multiple mechanisms may underlie the effect.

  
keywords          : "mutual exclusivity, disambiguation effect,  word learning, meta-analysis"
wordcount         : "X"

bibliography      : ["references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output:
  papaja::apa6_pdf:
    includes:
      after_body: appendix.tex
      
---

```{r load_packages, include = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(cache = F, echo = FALSE, message = FALSE,
                      warning = FALSE,  fig.pos = "tb", sanitize = T)

library(papaja)
library(tidyverse)
library(langcog)
library(ggthemes)
library(lme4)
library(knitr)
library(feather)
library(kableExtra)

source("helpers.R")
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```

```{r r-refs}
my_citations <- cite_r(file = "r-references.bib", 
                       pkgs = c("tidyverse", "lme4", "papaja", "metafor", "knitr"), 
                       withhold = FALSE,
                       footnote = TRUE)
```


# Introduction

A key property of language is that each word maps to a unique concept, and each concept maps to a unique word [@clark1987principle; bolinger1977meaning]. Like other regularities in language (e.g., grammatical categories), children cannot directly observe this one-to-one word-concept regularity, yet even very young children behave in a way that is consistent with it. The goal of this paper is develop a theory of the cognitive mechanisms underlying this behavior in children.

Evidence that children obey the one-to-one regularity comes from what is known as the “mutual exclusivity" (ME) effect (we return to the issue of nomenclature below). In a typical demonstration of this effect [@markman1988], children are presented with a novel and familiar object (e.g., a whisk and a ball), and are asked to identify the referent of a novel word ("Show me the dax"). Children in this task tend to choose the novel object as the referent, consistent with the one-to-one regularity in language (we refer to this paradigm throughout as the “ME paradigm”). A large body of work has demonstrated that this effect occurs in children across a wide range of ages, experimental paradigms, and populations [@mervis1994two;@golinkoff1994early;@markman2003;@halberda2003development;@bion2013fast].

The ME effect has received much attention in the word learning literature because the ability to identify the meaning of a word in ambiguous contexts is, in essence, the core problem of word learning. That is, given any referential context, the meaning of a word is underdetermined [@quine1960], and the challenge for the world learner is to identify the referent of the word within this ambiguous context. Critically, the ability to infer that a novel word maps to a novel object makes the problem much easier to solve. For example, suppose a child hears the novel word "kumquat" while in the produce aisle of the grocery store. There are an infinite number of possible meanings of this word given this referential context, but the child's ability to correctly disambiguate would lead her to rule out all meanings for which she already had a name. With this restricted hypothesis space, the child is more likely to identify the correct referent than if all objects in the context were considered as possible referents. 

Additionally, the ME effect has the potential to help the learner acquire words for multiple concepts that can be used to refer to the same object in the world, such as property names and object parts (e.g., “turquoise”, “handle”; @markman1988]). Consider a child who hears the novel word “turquoise” in the context of a turquoise colored ball. If the child obeys the one-to-one property of language and already knows the word “ball,”  the child may assume that “turquoise” refers to a property of the ball, such as color, rather than the ball itself. The one-to-one principle may be particularly useful for learning subordinate (e.g., “dalmation”) and superordinate labels (e.g. “animal”), since each instance of these labels is always consistent with concepts at all levels of the conceptual hierarchy (an observed dalmation is equally consistent with the labels “dalmation,” “dog” and “animal”; e.g., @waxman1986preschoolers). Unlike for property words, the child will never observe cross-situational evidence that would disambiguate among candidate concepts at different levels of the hierarchy. The one-to-one principle provides one possible route through which children might resolve this inherent ambiguity in word learning. 

Despite -- or perhaps due to -- the attention that the ME effect has received, there is little consensus regarding the cognitive mechanisms underlying it. Does it stem from a basic inductive bias on children's learning abilities ("constraint and bias accounts," see below), a learned regularity about the structure of language ("overhypothesis accounts"), reasoning about the goals of communication in context ("pragmatic accounts"), or perhaps some mixture of these? In the current paper, we lay out these possibilities and discuss the state of the evidence. Along the way we present a meta-analysis of the extant empirical literature. We then present two new, relatively large-sample developmental experiments that investigate the dependence of children's ME inferences on vocabulary (Experiment 1) and experience with particular words (Experiment 2). We end by discussing the emergence of ME inferences in a range of computational models of word learning.  We conclude that:

1. Explanations of ME are not themselves mutually exclusive and likely more than one is at play; *momen and merriman make this point
2. The balance of responsibility for behavior likely changes developmentally, with basic biases playing a greater role for younger children and learned overhypotheses playing a greater role for older children. 
3. All existing accounts put too little emphasis on the role of experience and strength of representation; this lack of explicit theory in many cases precludes definitive tests. 
4. ME inferences are distinct from learning.

### A note on terminology
@markman1988's seminal paper coined the term "mutual exclusivity," which was meant to label the theoretical proposal that "children constrain word meanings by assuming at first that words are mutually exclusive -- that each object will have one and only one label." [@markman1990, p.66]. That initial paper also adopted a task used by a variety of previous authors [including @golinkoff1985;@hutchinson1986children;@vincent-smith1974acquisition], in which a novel and a familiar object were presented to children in a pair and the child was asked to "show me the *x*," where *x* was a novel label. Since then, informal discussions have used the same name for the paradigm and effect (selecting the novel object as the referent of the novel word) as well as the theoretical account (an early assumption or bias). This conflation of paradigm/effect with theory is problematic, as other authors who have argued against the theoretical account then are in the awkward position of rejecting the name for the paradigm they have used. Other labels (e.g. "disambiguation" or "referent selection" effect) are not ideal, however, because they are not as specific do not refer as closely to the previous literature. Here we adopt the label "mutual exclusivity" (ME) for the general family of paradigms and associated effects, *without* prejudgment of the theoretical account of these effects. 

ME has also been referred to as "fast mapping." This conflation is confusing at best. In an early study, @carey1978 presented children with an incidental word learning scenario by using a novel color term to refer to an object: "You see those two trays over there. Bring me the *chromium* one. Not the red one, the *chromium* one." Those data [and subsequent replications, e.g. @markson1997] showed that this exposure was enough to establish some representation of the link between phonological form and meaning that endured over an extended period; a subsequent clarification of this theoretical claim emphasized that these initial meanings are partial [@carey2010]. Importantly, however, demonstrations of retention relied on learning in a case where there was a contrastive presentation of the word with a larger set of contrastive cues [@carey1978] or pre-exposure to the object [@markson1997]. 

## Theoretical Views on the ME effect
What are the cognitive mechanisms underlying the ME effect? A number of proposals have been made in the literature, many of which overlap or differ only in subtle ways. Here we briefly describe several influential proposals, highlighting the commonalities and differences across theoretical views.

### Constraint and bias accounts
Under constraint and bias accounts, children are argued to have a constraint or bias that is innate or emerges after very limited language input. One version of the account, proposed by Markman and colleagues [@markman1988;@markman2003], is that children have a constraint on the types of lexicons considered when learning the meaning of a new word -- a "mutual exclusivity constraint."  Under this constraint, children are biased to consider only those lexicons that have a one-to-one mapping between words and objects. Importantly, this constraint  is probabilistic and thus can be overcome in cases where it is incorrect (e.g. property names),  but it nonetheless serves to restrict the set of lexicons initially entertained when learning the meaning of a novel word. In principle, this constraint could be the result of either domain-specific or domain-general processes [@markman1992constraints]. As a domain general property, the ME constraint could be related to other cognitive mechanisms that lead learners to prefer one-to-one mappings (e.g. blocking and overshadowing in classical condition and the discounting principle in motivational research, [@lepper1973undermining]).

As formulated by Markman and colleagues, the ME constraint operates at the level of extensions (objects), not concepts. For example, the ME constraint says that the labels “policeman” and “cop” -- referring to the same entity in the world -- are violations of the constraint. Similarly, terms at different levels of the semantic hierarchy that can have the same extensions, such as “animal” and “dog,” are also seen as ME violations. In contrast, these cases are not violations in theories that posit the explanatory construct at the level of concepts (e.g., pragmatic accounts). The distinction between concepts and objects in each theoretical view is important for evaluating whether empirical evidence is consistent with a proposal. Note, however, that in the canonical ME paradigm, where the two referents are both different concepts and objects, the accounts at both levels make identical predictions.

A related proposal to the ME constraint is that children have a bias to map novelty to novelty [Novel-Name Nameless-Category principle (N3C); @golinkoff1994early @mervisbertrand2994; @mervis1994].  This principle differs from the ME constraint in that the rejection of  the familiar object as a potential referent is not part of the inference; instead, children are argued only to map the two novel elements to each other, the novel label and the object (thereby only implicitly rejecting the the familiar object as a referent for the novel label). The N3C principle is argued to be domain-specific to language.

Under a third account, children are motivated to identify objects for which they do not know a label for and fill the “lexical gap” with the novel label [@golinkoff1992].
Lexical Gap Filling: Merriman & Bowman (1989) 

### Probabilistic accounts
Probabilistic accounts contend that the ME effect does not derive from an explicit representation related to the one-to-one regularity, as proposed by the constraints and bias accounts; rather, under these accounts,  the effect is the product of a word learning system that tracks the frequency of exemplars of words and their referents over time, and then reasons probabilistically about the most likely referent for a novel word within the referential context. [@regier2005emergence;@mcmurray2012;@frank2009using;@fazly2010probabilistic;@macwhinneycompetition].

### Pragmatic accounts
Under pragmatic accounts, the ME effect derives from reasoning about the intention of the speaker within the referential context [@clark1987principle; @clark1988principle; @clark1990principle; @diesendruck2001]. The critical aspect of this account is the claim that children assume that “every two forms contrast in meaning” (Clark, 1988, p. 417), or the "Principle of Contrast.” Clark also argues that speakers hold a second assumption -- that speakers within the same speech community use the same words to refer to the same objects ("Principle of Conventionality"). The ME effect then emerges from the interaction of these two principles. That is, the child reason’s implicitly: You used a word I've never heard before. Since, presumably we both call a ball "ball" and if you'd meant the ball you would have said "ball," this new word must refer to the new object. Clark (1988, 1990) argues that these two principles are learned, but emerge from a more general understanding that other people have intentions [@grice1977logic, @carpenter1988social].

### Logical inference accounts
@halberda2003development argues that the ME effect is the result of domain-general processes used for logical reasoning.  Under this proposal, children are argued to be solving a disjunctive syllogism (“A or B, not A, therefore B”) by rejecting labels for known objects. For example, upon hearing the novel label “dax,” the child would implicitly reason that the referent could be either object A or B, and then reject object A because it already has a known label. By deduction, the child would then conclude that “dax” refers to object B. This account shares the same formal reasoning structure as pragmatic accounts, but differs in the underlying source of the key inference: While pragmatic accounts argue that children conclude that object B must be the referent on the basis of reasoning about intention, the logical inference account proposes that this same inference is made on the basis of logical reasoning.

### Over-hypothesis accounts
@lewis2013b suggest that the ME effect could emerge by learning from the statistics of the child’s linguistic. That is, given evidence that words tend to refer to a single concept, the child might develop a learned "overhypothesis"  [@kemp] that the lexicon is structured such that each concept is associated with one and only one label. The learning mechanisms are argued to be probabilistic and domain general, while the learned overhypothesis is specific to the structure of the lexicon. The emergent overhypothesis about the structure of the lexicon would be similar to the knowledge a learner is proposed to have under the constraints and biases account. 

In order for learning to get off the ground, however, children must notice the one-to-one mapping between a word and a concept in the context of a particular instances of a label’s usage.  @lewis2013b suggest that this ability could derive from a variety of different mechanisms that make use of the structure of the learning task, such as pragmatic, probabilistic, and logical inference accounts. @merriman1986some make a similar proposal, but argue that the overhypothesis is learned primarily from explicit parental corrections (e.g., “that’s an apple, not an orange”).

Under the overhypothesis account, then, the ME effect emerges from multiple mechanisms at two different timescales -- one as a function of information about the pragmatic or inferential structure of the communicative context and one as a function of learned higher-order knowledge about how the lexicon is structured. Both mechanisms would then contribute to the inference with different weights across development and across children.

## Theory-Constraining Findings
The literature on the ME effect explores predictions of a variety of theoretical proposals. Here, we highlight of few of the key findings that provide important constraints for a theory of the ME effect.

### Developmental change 
A number of studies provide evidence that the strength of the ME effect increases across development [e.g. @halbdera2003, @merriman1986some, @bion2013fast]. For example, [@halberda2003] tests 14- 16- and 17- mo in the ME paradigm, and finds a pattern of developmental change: 14 mo children are biased to select the familiar object, 16-mo were at chance, and 17-mo were biased to select the novel object, consistent with the one-to-one principle. This evidence suggests that the strength of the ME effect changes across development, though the underlying cause of this developmental change is an open question (an issue we return to below).

### Multilingualism
Children who are learning multiple languages have been tested in the ME paradigm in order to examine the role of linguistic input in the ME effect. Multilingual children are an interesting test population because the one-to-one mapping between words and concepts is arguably violated in their linguistic input (e.g. a child learning Spanish might know both the words “ball” and “pelota” for the concept ball). Thus, if the ME effect is independent of lexical input, then multilingual children should perform on the ME task siimiliar to monolingual children whose input does not violate the one-to-one assumption. In contrast to this prediction, Byers-Heinlein [@btersheinline] and others find that multilingual children select the novel object at lower rates than monolingual children, suggesting that lexical input plays a role in the strength of the ME effect.

### Speaker-change studies
Some evidence for pragmatic accounts comes from experiments in which children must reason about the intent of the speaker directly. In one set of experiments [@diesendruck2005principles], children were taught a novel label for a creature that is either a common noun or a proper noun. A speaker, who was not present during the teaching phase, then requests a create by either a novel label. If children are reasoning about the knowledge of the speaker, the pragmatic account predicts that the speaker should know the common name for the known creature (as a competent speaker of the language), but not the proper name. Children show a pattern consistent with this prediction by selecting a novel creature in a 2-AFC task when taught the common noun label, but not a proper noun label.

### Autism 
Children with autism are known to have impairments  in reasoning about the intentions of others [@baron1986mechanical]. As such, this population has been tested in the ME paradigm to examine the extent to which reasoning about the intentions of other speakers, as required by the pragmatic view, is a necessary component of the ME effect. Evidence suggests (e.g. [@preissler2005role;@de2011mutual]) that children with autism select the novel object in the ME task at similar rates to typically developing children, suggesting that pragmatic reasoning is unlikely to be a necessary component for the ME effect.

### Fast mapping + no retention
<!-- not sure about this-->

### NF vs. NN
The canonical ME paradigm involves an object with a known label and an object with an unknown label. In this paradigm, evidence that children are biased to select the novel referent when presented with a novel word is consistent both with accounts that argues that children *reject* the familiar object (e.g. Constraint and bias accounts) and with accounts that children are biased to map the novel word to the novel object (N3C principle). To distinguish between these two types of accounts, researchers have compared the canonical ME paradigm that uses a novel and a familiar object (NF design) to a paradigm that uses two novel objects (NN design). In the NN variant, the child is presented with two novel objects but taught a novel label for one of the objects unambiguously (“This is a zot”). Then, the child is asked to identify the referent of a second novel label (“Can you find the fep?”). If the child relies on novelty alone to identify the correct referent, the ME effect should be absent in the NN design since both objects are novel the child. Instead, there is evidence to suggest that children show the ME effect in both NN and NF designs [e.g., @diesendruck2001;@de2001mutual], suggesting that a novelty bias is not sufficient to account for the ME effect.

## Synthesis

To summarize, the empirical findings that a successful theory of ME must account for are:
- why the effect is present in young children, but gets larger with development (developmental change);
- how language experience supports the effect (multilingualism evidence);
- why pragmatic reasoning can support the effect (speaker change evidence), but why it is not necessary (autism evidence). 

In developing a successful theory, it is important to note that the theoretical accounts of mechanisms underlying the ME effect that have proposed in the literature are not mutually exclusive with each other [@momen2002two]. As pointed out by Markman [@markman1992constraints], testing different mechanisms in isolation is the result of an experimental approach to theory building, rather than a reflection of an assumption that there exists one and only one mechanism underlying the effect. That is, in order to identify whether a mechanism is *sufficient* to give rise to the ME effect, logical researchers design experiments in which the ME effect can be observed only if a particular cognitive mechanism is sufficient for the effect. If the effect is observed under these conditions, it provides evidence only that the mechanism is sufficient for the effect, but not that it is necessary and not that other mechanisms are not also sufficient. Indeed, there is reason to think that redundancy in mechanisms for the same behavior is a desirable property of a cognitive system [@markman1992constraints]. 

Instead, in light of the full body of evidence, we argue that multiple mechanisms likely support the ME effect probabilistically. Each child may be making use of multiple mechanisms with varying weights across development and situations, and the relative weights of these different mechanisms may vary across children. For example, learners may be making use of both general knowledge about how the lexicon is structured as well as information about the pragmatic or inferential structure of the task, and both of these sources of information support the ME inference.

## The Current Study
A theory of the ME effect that appeals to multiple cognitive mechanisms is a difficult theory to build. This is because that, in order to build such a theory, we must gather empirical evidence that not only describes *that* a mechanism underlies a behavior, but also the degree to which it does and how the contribution of different mechanisms varies across tasks, developmental ages and populations. The goal of the current study is to contribute to building such a theory in two ways. First,  we first provide a quantitative synthesis of the current literature related to  the ME effect in the form of a meta-analysis. The meta-analysis allows us to gain a clearer picture of the empirical landscape in terms of the magnitude of the effect as well as the role of moderating variables. Second, we present two experiments that examine the causal role of an understudied moderator in the literature -- linguistic experience. In Experiment 1, we examine the relationship between vocabulary size and the strength of the ME effect on a large sample of children. We find evidence that children with larger vocabularies tend to show a stronger ME effect, consistent with the notion that  language experience influences the ME effect. In Experiment 2, we more directly test the hypothesis that language experience plays a *causal* role in the ME effect, by directly manipulating children's amount of experience with a word. We find greater experience with the familiar word in the ME paradigm leads to a stronger ME effect. We conclude by re-evaluating a theory of the ME effect in light of our new evidence.


```{r child = "sections/ma_writeup.Rmd"}
```

```{r child = "sections/exp1_writeup.Rmd"}
```

```{r child = "sections/exp2_writeup.Rmd"}
# EXCLUDED FOR NOW: child = "sections/model_writeup.Rmd" 
```

# General Discussion


Potential sources of developmental change
Cognitive limitations mean that you just don’t think of the other object when one is named (Merriman 1986b) - better at coordinating concepts (related to Flavell, though not the same….he actually argues the opposite)..
Perceptual experience - Merriman 1986b
Linguistic input
Mervis 1987 - not till children accept parents authority
Time constraint - Frank (Halberda)



\newpage

# References

```{r session info, include = F}
sessionInfo() %>% pander::pander(compact = F)
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r}
r_refs(file = "r-references.bib")
render_appendix("appendix.Rmd")
```
