---
title             : "The role of developmental change and linguistic experience in the mutual exclusivity effect"
shorttitle        : "Development and experience in mutual exclusivity"

author: 
  - name          : "Molly Lewis"
    affiliation   : "1,2"
    corresponding : yes    # MUST define one corresponding author
    address       : "5735 S Ellis Ave, Chicago, IL 60637"
    email         : "mollyllewis@gmail.com"
  - name          : "Veronica Cristiano"
    affiliation   : "3"
  - name          : "Brenden M. Lake"
    affiliation   : "4,5"
  - name          : "Tammy Kwan"
    affiliation   : "4,5"
  - name          : "Michael C. Frank"
    affiliation   : "6"
  
affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "University of Wisconsin-Madison"
  - id            : "3"
    institution   : "Gallaudet University"
  - id            : "4"
    institution   : "New York University"
  - id            : "5"
    institution   : "Cognitive ToyBox, Inc."
  - id            : "6"
    institution   : "Stanford University"
    
author_note: |
  We would like to thank support from Cognitive ToyBox, and note that BML and TK are co-founders of Cognitive ToyBox which developed the two tablet applications in Experiment 1. Data from Experiment 2 were previously presented in the Proceedings of the Cognitive Science Society Conference in Lewis & Frank (2013).
  
abstract: |
  Given a novel word and a familiar and a novel referent, children have a bias to assume the novel word refers to the novel referent. This bias -- often referred to as the "Mutual Exclusivity" (ME) effect -- is thought to be a potentially powerful route through which children might learn new word meanings, and,  consequently, has been the focus of a large amount of empirical study and theorizing. Here, we focus on two aspects  of the effect that have received relatively little attention in the literature: Development and experience. In particular, we characterize change in the strength of the effect across development, and investigate the role that linguistic experience plays in this developmental change. We first summarize the current body of empirical findings via a meta-analysis, and then present two experiments that examine the relationship between a child's amount of linguistic experience and the strength of the ME effect. We conclude that the strength of the effect varies dramatically across development and that linguistic experience is likely one causal factor contributing to this change. In the General Discussion,  we describe how existing theories of ME can account for our findings, and highlight the value of computational modeling for future theorizing.
  

keywords          : "mutual exclusivity, disambiguation effect,  word learning, meta-analysis"

wordcount         : "approx. 9200"
bibliography      : "references.bib"
csl               : "apa6-meta.csl"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
documentclass     : "apa6"
lang              : "english"
class             : "man"
output:
  papaja::apa6_pdf:
    includes:
      after_body: appendix.tex
---


```{r load_packages, include = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = FALSE, message = FALSE,
                      warning = FALSE,  fig.pos = "t!", sanitize = TRUE)

library(papaja)
library(tidyverse)
library(langcog)
library(ggthemes)
library(lme4)
library(knitr)
library(feather)
library(kableExtra)
library(metafor)
library(broom)
library(citr)
library(here)
source(here("writeup/journal_paper/helpers.R"))
```

```{r analysis_preferences}
set.seed(42) # seed for random number generation
```

```{r r-refs}
my_citations <- cite_r(file = "r-references.bib", 
                       pkgs = c("tidyverse", "lme4", "papaja", 
                                "metafor", "knitr"), 
                       withhold = FALSE,
                       footnote = TRUE)
options(citr.parent_documents = "me_vocab_main.Rmd", # this allows you to use citr from child rmds (which is necessary to put asterick in bibliography)
        scipen = 999)  # turn off scientific notation for printing reasons
```


# Introduction

A key property of language is that words tend to have distinct meanings, and concepts tend to be referred to via unique words [@clark1987principle; @bolinger1977meaning]. Like a whole host of other regularities in language -- for example, the existence of abstract syntactic categories -- children cannot directly observe the tendency for one-to-one word-concept mapping, yet even very young children behave in a way that is consistent with it. Evidence that children obey the one-to-one regularity comes from what is known as the “mutual exclusivity" (ME) effect. In a typical demonstration of this effect [@markman1988], children are presented with a novel and familiar object (e.g., a whisk and a ball), and are asked to identify the referent of a novel word ("Show me the dax"). Children across a wide range of ages, experimental paradigms, and populations tend to choose the novel object as the referent in this task [@mervis1994two;@golinkoff1994early;@markman2003;@halberda2003development;@bion2013fast]. The goal of the current paper is to review and synthesize evidence for an aspect of the mutual exclusivity behavior that has received relatively little attention in the literature: the role of development and experience.

Before engaging with the prior literature related to this behavior, it is useful to first make several theoretical distinctions and clarify terminology. @markman1988's seminal paper coined the term "mutual exclusivity," which was meant to label the theoretical proposal that "children constrain word meanings by assuming at first that words are mutually exclusive -- that each object will have one and only one label." [@markman1990, p.66]. That initial paper also adopted a task used by a variety of previous authors [including @golinkoff1985;@hutchinson1986children;@vincent-smith1974acquisition], in which a novel and a familiar object were presented to children in a pair and the child was asked to "show me the *x*," where *x* was a novel label. Since then, informal discussions have used the same name for the paradigm (this precise experiment), inference (the ability to disambiguate the novel word), and the effect (the fact that children select the novel object as the referent). Further, the same name is also often used as a tag for a particular theoretical account (an early assumption or bias regarding the one-to-one nature of the lexicon). This conflation of paradigm/effect with theory is problematic, as authors who have argued against the specific theoretical account then are in the awkward position of rejecting the name for the paradigm they themselves have used. Other labels (e.g. "disambiguation" or "referent selection" effect) are not ideal, however because they are not as specific and do not refer as closely to the previous literature. 

ME has also been referred to as "fast mapping" in the literature. We believe that this label is confusing because it conflates two distinct ideas. In an early study, @carey1978 presented children with an incidental word learning scenario by using a novel color term to refer to an object: "You see those two trays over there. Bring me the *chromium* one. Not the red one, the *chromium* one." Those data [and subsequent replications, e.g. @markson1997] showed that this type of exposure was enough for the child to establish some representation of the link between the phonological form of the novel word and meaning that endured over an extended period; a subsequent clarification of this theoretical claim emphasized that these initial meanings are partial [@carey2010]. Importantly, however, demonstrations of retention relied on learning in the case of contrastive presentation of the word with a larger set of contrastive cues [@carey1978] or pre-exposure to the object [@markson1997]. 

Further, the "fast mapping" label has been the focus of critique due to findings by @horst2008 that young children do not always retain the mappings that result from the ME inference. In this work, children were presented with a novel word and asked to identify the referent in the ME paradigm, and they generally succeeded in making the correct inference (selecting the novel object). However, when asked to recall the referent of the same label after a short 5-min delay, children performed poorly. This pattern of results suggests an important distinction between making the ME inference in the context of the ME paradigm, and actually learning the meaning of the novel word such that it can be recalled later beyond the context of the ME paradigm. Our work here focuses only on the more narrow question of how children make the inference in the context of the ME paradigm. 

Here we adopt the label "mutual exclusivity" (ME) effect as a generic term referring to the empirical finding that young children tend to map a novel word to a novel object. We distinguish the ME effect from the family of experimental paradigms that demonstrate the effect, which we refer to as "ME paradigms." Further, we distinguish the paradigm and the associated effect from the cognitive inference made by children that leads to the ME effect ("ME inference").  Each of these are in turn distinguished from theories which seek to explain the ME inference ("ME theory"). In all of these cases, we use the term "mutual exclusivity" as convenient nomenclature but do so *without* prejudgement of the theoretical account.

The ME effect has received much attention in the word learning literature because the ability to identify the meaning of a word in ambiguous contexts is, in essence, the core problem of word learning. That is, given any referential context, the meaning of a word is underdetermined [@quine1960], and the challenge for the world learner is to identify the referent of the word within this ambiguous context. For example, suppose a child hears the novel word "kumquat" while in the produce aisle of the grocery store. There are an infinite number of possible meanings of this word given this referential context, but the ability to make a ME inference would lead her to rule out all meanings for which she already had a name. With this restricted space of possibilities, she is more likely to identify the correct referent than if all objects in the context were considered as candidate referents. 

Being able to make an ME inference could also help children acquire words for multiple words that can be used to refer to the same object in the world, even though they actually refer to different concepts [for example, property names and object parts such as “turquoise” and “handle"; @markman1988]. Consider a child who hears the novel word “turquoise” in the context of a turquoise-colored ball. If she obeys the one-to-one property of language and already knows the word “ball,” the child may assume that “turquoise” refers to a property of the ball, such as color, rather than the ball itself. Of course, seeing evidence about the meaning of "turquoise" across multiple different turquoise reference situations would further support the inference [referred to as "cross-situational evidence"; @yu2007rapid].

Making ME inferences could be particularly useful for learning subordinate (e.g., “dalmation”) and superordinate labels (e.g., “animal”). Subordinate and superodinate labels present a particular challenge to the learner since each instance of these labels is always consistent with concepts at all levels of the conceptual hierarchy [an observed dalmation is equally consistent with the labels “dalmation,” “dog” and “animal”; e.g., @waxman1986preschoolers]. Also, and unlike in the case of property words, a child will never observe cross-situational evidence that disambiguates among candidate concepts at different levels of the hierarchy. Thus ME inferences provide one possible route through which children might resolve this inherent ambiguity in word learning. 

Despite -- or perhaps due to -- the attention that the ME effect (and the related consequences of making ME inferences) has received, there is little consensus regarding the cognitive mechanisms underlying it. Does it stem from a basic inductive bias on children's learning abilities ("constraint and bias accounts," "probabilistic accounts," and "logical inference accounts"), a learned regularity about the structure of language ("overhypothesis accounts"), reasoning about the goals of communication in context ("pragmatic accounts"), or perhaps some mixture of these? Across the literature, researchers have tested a variety of populations of children and used a wide range of different paradigms in order to discriminate between these theories, and a successful theory of ME will need to be able to account for this wide range of empirical phenomena.

In the current paper, our goal is to present evidence for one particular pattern of findings related to ME that has played a relatively minor role in theorizing about ME: Developmental change in the magnitude of the effect. Characterizing developmental change is important because it provides a key constraint on theoretical accounts of ME. Namely, change in the magnitude of the ME effect must be due either to maturational change or the child's increasing experience with the world, or both. In our work here, we focus on characterizing the link between developmental change and one type of experience -- linguistic experience. There are a variety of ways that linguistic experience could support the ME inference. For example, a child who knows more words in general might be more likely to know the familiar word in the ME task, and therefore more likely to select the novel object. Alternatively, linguistic experience might allow children to learn generalities about how language is used that could be helpful in making the ME inference, such as general pragmatic reasoning or an understanding of the one-to-one regularity in language. Our aim here is not to definitively discriminate between theories of ME, but rather present evidence for a causal role of experience in the ME effect that can provide a constraint on existing theories of ME. In the General Discussion, we consider in more detail how existing theories of ME might account for our findings.

Across the literature on ME,  the primary focus of theorizing has been on accounting for why children at one or a few timepoints in development behave in a way that is consistent or not with the ME effect, rather than for development change in effect strength. In part, this focus may be due to methodological challenges in conducting developmental experiments rather than to an underlying theoretical motivation: since data collection from young children is expensive, it is costly for researchers to collect data from children across more than a couple ages groups. In addition, experimental evidence from the ME paradigm is typically summarized as a binary description (children's "success" or "failure" in the ME task) rather than as a more continuous estimate of the effect, and this methodological choice may obscure evidence of more subtle changes in the cognitive system across development.

There are, however, a handful of studies that show developmental change in the mutual exclusivity effect by testing multiple age groups within the same experiment (e.g., Bion et al., 2013; Halberda, 2003; W. E. Merriman, 1986). For example, @halberda2003development tests 14- 16- and 17- mo in the ME paradigm, and finds a pattern of developmental change: 14-mo children were biased to select the familiar object, 16-mo were at chance, and 17-mo were biased to select the novel object, demonstrating the ME effect. While multi-age-group studies such as this  provide clear evidence *that* there is developmental change, they do not provide the type of quantitative description of its developmental trajectory of the effect that could provide an important constraint on theories of ME. 

## The Current Study
We first describe the state of the evidence for developmental change in the ME effect via a meta-analysis of the extant empirical literature. By aggregating across studies that each test different ages, the meta-analytic approach allows us to take advantage of the large number of studies already conducted on the ME effect in order to characterize developmental change. We then present two new, relatively large-sample developmental experiments that investigate the causal role of linguistic experience in contributing to the ME effect. In Experiment 1, we examine the relationship between vocabulary size and the strength of the ME effect on a large sample of children. We find evidence that children with larger vocabularies tend to show a stronger ME effect, consistent with the notion that language experience influences the ME effect. In Experiment 2, we test the hypothesis that language experience plays a *causal* role in the ME effect, by directly manipulating children's amount of experience with a word. We find greater experience with the familiar word in the ME paradigm leads to a stronger ME effect.  In the General Discussion, we conclude by discussing the role of developmental change and experience in the context of candidate theories of ME, in the context of our evidence.

```{r child = "sections/ma_writeup.Rmd"}
```

```{r child = "sections/exp1_writeup.Rmd"}
```

```{r child = "sections/exp2_writeup.Rmd"}
```

# General Discussion

We set out to measure developmental and experience-based shifts in children's ability to make ME inferences. Across a systematic meta-analysis of the existing literature and two new studies, we found strong evidence that older children make stronger and more reliable ME inferences than younger children. Further, both the meta-analytic findings and the results of Experiment 1 suggest that vocabulary size is related to ME performance, perhaps moreso than age. Finally, Experiment 2 showed that ME inference strength is also directly influenced by children's familiarity with the alternative objects and their labels. Taken together, this body of evidence suggests that the ability to make ME inferences changes very substantially with development and experience, changes that have been under-appreciated due to the limited size and developmental range of most of the studies of this phenomenon. 


## The role of development in theories of the ME effect

We next turn to the implications of these findings for theories of ME. The literature contains a large number of proposals for the mechanisms supporting ME, and many of these overlap or differ only in subtle ways. Here we briefly describe several influential proposals, highlighting the commonalities and differences across theoretical views and considering the ways they could accommodate our findings. To summarise our conclusion, developmental and experience-based changes in the strength of the ME inference are not *inconsistent* with many possible theoretical alternatives in the sense that there are not clear predictions that a specific ability would *not* develop. Instead, most theories simply have not discussed the predicted developmental course of the ME inference explicitly; developmental and experience-based change are auxiliary to the theory. In contrast, computational models of word learning -- as learning models -- make clear and explicit predictions about the role of experience. Given this, our work here suggests that such models may provide a more parsimonious framework for thinking about ME. 

### Constraint and bias accounts

One influential proposal regarding the sources of ME inferences is that children have a constraint that is innate or early-emerging. Under one version of this account [@markman1988;@markman2003], children have a constraint on the types of lexicons considered when learning the meaning of a new word -- a "mutual exclusivity constraint." Under this constraint, children are biased to consider only those lexicons that have a one-to-one mapping between words and objects. Importantly, this constraint is probabilistic and thus can be overcome in cases where it is incorrect (e.g., property names or super-/sub-ordinate labels), but it nonetheless serves to restrict the set of lexicons initially entertained when learning the meaning of a novel word. In principle, this constraint could be the result of either domain-specific or domain-general processes [@markman1992constraints]. As a domain general property, the ME constraint could be related to other cognitive mechanisms that lead learners to prefer one-to-one mappings [e.g., blocking and overshadowing in classical condition and the discounting principle in motivational research; @lepper1973undermining].

This classic constraint-based theory of ME does not have an obvious role for the developmental and experiential effects we have documented here. Since even young children are posited to have some bias, on such a theory, developmental effects on this kind of theory would be primarily generated by changes in downstream, performance-based factors (for example, the ability to attend to the experimental task). Further, experience-based effects such as those observed in our Experiment 2 could be the result of individual children simply failing to access individual lexical representations. These modifications to constraint theories are ad-hoc (but perhaps not unreasonable). 

Another related constraint-based proposal is the Novel-Name Nameless-Category principle [N3C; @golinkoff1994early; @mervis1994acquisition]. On the N3C account, the rejection of the familiar object as a potential referent is not part of the inference. Instead, children are argued only to map the two novel elements to each other, the novel label and the object (thereby only implicitly rejecting the the familiar object as a referent for the novel label).  Unlike the ME constraint, the N3C principle was argued (based on the empirical finding of developmental change) to emerge developmentally with language experience. Nevertheless, the specific developmental prediction was that N3C became available after children went through a "vocabulary spurt" rather than emerging gradually and continuing to increase in strength (as we observed). Further, this account does not have an account of specific experiences with particular words, the effect we observed Experiment 2. 

<!-- n the first account, children are motivated to identify objects for which they do not know a label and fill that "lexical gap" with the novel label [@golinkoff1992young; @merriman1989mutual]. HOW DOES THIS DIFFER FROM N3C -->

### Pragmatic contrast accounts

One important alternative to principle-based accounts are pragmatic accounts. Under these accounts, the ME inference derives from reasoning about the intention of the speaker within the current referential context [@clark1987principle; @clark1988logic; @clark1990pragmatics; @diesendruck2001]. The critical aspect of this account is the claim that children assume that "every two forms contrast in meaning" (Clark, 1988, p. 417), or the "Principle of Contrast." Clark also argues that speakers hold a second assumption -- that speakers within the same speech community use the same words to refer to the same objects ("Principle of Conventionality"). The ME effect then emerges from the interaction of these two principles. That is, the child reason’s implicitly: You used a word I've never heard before. Since, presumably we both call a ball "ball" and if you'd meant the ball you would have said "ball," this new word must refer to the new object. Clark (1988, 1990) argues that these two principles are learned, but emerge from a more general understanding that other people have intentions [@grice1975logic; @tomasello2005search].

Although developmental and experience-based effects were not a specific focus of these accounts, these findings are relatively easy to accommodate within this framework. A pragmatic theorist could simply argue that children's understanding of each of these principles is changing across the relevant time period [@clark2010]. Experiential effects similarly are not accounted for in this framework, but could be added as an auxiliary assumption. 

### Logical inference accounts

@halberda2003development argues that the ME effect is the result of domain-general processes used for logical reasoning. Under this proposal, children are argued to be solving a disjunctive syllogism ("A or B, not A, therefore B") by rejecting labels for known objects. For example, upon hearing the novel label "dax," the child would implicitly reason that the referent could be either object A or B, and then reject object A because it already has a known label. By deduction, the child would then conclude that “dax” refers to object B. This account shares the same formal reasoning structure as pragmatic accounts, but differs in the underlying source of the key inference: While pragmatic accounts argue that children conclude that object B must be the referent on the basis of reasoning about intention, the logical inference account proposes that this same inference is made on the basis of logical reasoning.

Although this proposal was formulated on the basis of developmental data showing failures at 14 months (with an interesting pattern of alternative behavior), there is no account provided for what sorts of developmental changes or experiences lead to the emergence of disjunctive syllogism. Indeed, syllogistic reasoning of this sort is argued to be available even in younger children [@cesana-arlotti2018;@halberda2018]. If so, again, auxiliary theoretical assumptions are required to specify the specific maturational processes or developmental experiences that lead the inference to become available for older children. 

### Probabilistic accounts

Probabilistic computational accounts contend that ME does not derive from an explicit representation of a constraint or principle nor from pragmatic reasoning, as proposed by other accounts. Rather, under this broad class of accounts accounts, the ME inference is the product of a word learning system that tracks the frequency of words and their referents over time, and then uses probabilistic associative mechanisms to infer novel word-referent mappings. 

There are a wide variety of computational models that instantiate such ideas. For example, in an early model @regier2005emergence used an associative exemplar model to account for a variety of influential findings in early word learning including the ME inference. Under this model, second labels are hard to learn due to memory interference (and hence novel labels are preferentially mapped to new referents). Similarly, in the model of @frank2009using, a set of simple parsimony biases lead the model to assume that it is more likely that a novel word would have been used to refer to a novel referent (rather than a familiar word also having a second meaning that was never used). While the details vary for other models, the general set of principles in operation is similar in models by e.g., @mcmurray2012, @fazly2010probabilistic, and @kachergis2012. 

Unlike the largely verbal theories described above, these computational models allow the evaluation of both developmental and experiential effects. In fact, the findings of our meta-analysis and Experiments 1 and 2 should emerge in some form from nearly all of the computational models mentioned above. For example, the strength of the ME inference in the model of @frank2009using is directly proportional to the number of observations of the familiar word. Thus, more experience with language will lead to more robust representations of familiar words and stronger ME inferences. Similarly, within the framework of Experiment 2, the number of experiences with the first novel word should mediate the strength of the inference to the second [this finding is demonstrated through simulation in a related model by @lewis2013b]. In general, these computational models posit that ME inferences emerge from computations over graded representations. These representations could be graded, memory representations [@regier2005emergence;@kachergis2012] or neural network weights [@mcmurray2012]; they could also be probabilities in a more explicit representation of the lexicon [@frank2009using;@fazly2010probabilistic]. 

The broader point is that, on most of the verbal theories described above, developmental and experience-based changes in ME are auxiliary to the core theory of the phenomenon. Even those theories that have some role for development only discuss the notion of developmental emergence based on a linguistic generalization or a vocabulary milestone. In contrast, each of these computational theories is a learning theory: it takes experience with a particular stimulus as a core part of the theory. Thus, our findings are much more clearly captured by the computational literature on modeling early word learning than by the verbal theories that preceded it. 

The next step in this literature -- one that we hope is provoked by our work -- is to explore quantitative fits to specific developmental patterns. While all of the models described above can in principle provide quantitative predictions, in practice it will take significant work to create a fair comparison of the shape of these predictions to the trends we observed here. Such quantitative modeling of developmental change would provide a powerful step forward in terms of using insights from the literature to predict variation amongst children. 

## Conclusions

Our theorizing about word learning has often taken as the primary phenomenon the emergence of a particular phenomenon. The associated theorizing then often provides only a relatively small part for further developmental change, if any at all. Similarly, while no theorist would deny the importance of experience with a particular stimulus as moderating a specific experimental effect, these experiences are rarely core to the theory being developed. In contrast, in our survey of the literature and our experiments, we found that both experience and development were key quantitative determinants of children's ability to perform the ME inference. Thus, such models provide a parsimonious starting point for reasoning about the origins of ME. Further, and more broadly, the development of explicit computational theories provides a route to incorporate developmental experience more explicitly into our theorizing. 


\newpage

# References


\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r}
r_refs(file = "r-references.bib")
render_appendix("appendix.Rmd")
```
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
References marked with an asterisk indicate studies included in the meta-analysis.
<div id = "refs"></div>
\endgroup

---
nocite: | 
  @preissler2005role, @ de_Marchena_2011, @byers2009monolingual, @Byers_Heinlein_2013, @DAVIDSON_1997, @Houston_Price_2010, @Lederberg_2000, @markman2003, @Mather_2009, @Graham_1998, @horst2008, @Horst_2010, @bion2013fast, @DE_K_2001, @Frank_2016, @Gollek_2016, @Grassmann_2010, @Grassmann_2015, @halberda2003development, @HALBERDA_2006, @markman1988, @EVEY_1998, @merriman1989mutual, @Merriman_1991, @Merriman_1995, @momen2002two, @White_2008, @Merriman_1993, @Scofield_2009, @Sugimura_1996, @vincent-smith1974acquisition, @diesendruck2001, @Kalashnikova_2016, @Allen_2010, @Wall_2015, @SCOFIELD_2007, @bedford2013failure, @beverly2003fast, @choi2014korean, @estis2015children, @frank1999, @graham2010role, @hollich2000, @jarvis2004input, @kalashnikova2016flexible, @mervis1995acquisition, @merriman1986some
...

