---
title             : "Developmental change and experience in the mutual exclusivity effect"
shorttitle        : "Development and experience in mutual exclusivity"

author: 
  - name          : "Molly Lewis"
    affiliation   : "1, 6"
    corresponding : no    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Veronica Cristiano"
    affiliation   : "2"
  - name          : "Brenden Lake"
    affiliation   : "3"
  - name          : "Tammy Kwan"
    affiliation   : "4"
  - name          : "Michael C. Frank"
    affiliation   : "5"
  
affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "Gallaudet University"
  - id            : "3"
    institution   : "New York University"
  - id            : "4"
    institution   : "Cognitive Toybox, Inc."
  - id            : "5"
    institution   : "Stanford University"
  - id            : "6"
    institution   : "University of Wisconsin-Madison"

authornote: |
  Data from Experiment 2 were previously presented in the Proceedings of the Cognitive Science Society Conference in Lewis & Frank (2013). 
    $^*$To whom correspondence should be addressed. E-mail: mollyllewis@gmail.com
    
abstract: | 

keywords          : "mutual exclusivity, disambiguation effect,  word learning, meta-analysis"
wordcount         : "X"

bibliography      : ["references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
lang              : "english"
class             : "man"
output:
  papaja::apa6_pdf:
    includes:
      after_body: appendix.tex
---


```{r load_packages, include = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = FALSE, message = FALSE,
                      warning = FALSE,  fig.pos = "tb", sanitize = TRUE)
library(papaja)
library(tidyverse)
library(langcog)
library(ggthemes)
library(lme4)
library(knitr)
library(feather)
library(kableExtra)
library(metafor)
library(broom)
source("helpers.R")
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```

```{r r-refs}
my_citations <- cite_r(file = "r-references.bib", 
                       pkgs = c("tidyverse", "lme4", "papaja", 
                                "metafor", "knitr"), 
                       withhold = FALSE,
                       footnote = TRUE)
```


# Introduction

A key property of language is that words tend to have distinct meanings, and concepts tend to be referred to via unique words [@clark1987principle; @bolinger1977meaning]. Like a whole host of other regularities in language -- for example, the existence of abstract syntactic categories -- children cannot directly observe the tendency for one-to-one word-concept mapping, yet even very young children behave in a way that is consistent with it. Evidence that children obey the one-to-one regularity comes from what is known as the “mutual exclusivity" (ME) effect. In a typical demonstration of this effect [@markman1988], children are presented with a novel and familiar object (e.g., a whisk and a ball), and are asked to identify the referent of a novel word ("Show me the dax"). Children across a wide range of ages, experimental paradigms, and populations tend to choose the novel object as the referent in this task [@mervis1994two;@golinkoff1994early;@markman2003;@halberda2003development;@bion2013fast]. The goal of this paper is to review and synthesize evidence for an aspect of the mutual exclusivity behavior that has received relatively little attention in the literature: the role of experience and development.

Before engaging with the prior literature related this behavior, it is useful to first make several theoretical distinctions and clarify terminimology. @markman1988's seminal paper coined the term "mutual exclusivity," which was meant to label the theoretical proposal that "children constrain word meanings by assuming at first that words are mutually exclusive -- that each object will have one and only one label." [@markman1990, p.66]. That initial paper also adopted a task used by a variety of previous authors [including @golinkoff1985;@hutchinson1986children;@vincent-smith1974acquisition], in which a novel and a familiar object were presented to children in a pair and the child was asked to "show me the *x*," where *x* was a novel label. Since then, informal discussions have used the same name for the paradigm (this precise experiment), inference (the ability to disambiguate the novel word), and the effect (the fact that children select the novel object as the referent). Further, the same name is also often used as a tag for a particular theoretical account (an early assumption or bias regarding the one-to-one nature of the lexicon). This conflation of paradigm/effect with theory is problematic, as authors who have argued against the specific theoretical account then are in the awkward position of rejecting the name for the paradigm they themselves have used. Other labels (e.g. "disambiguation" or "referent selection" effect) are not ideal, however because they are not as specific and do not refer as closely to the previous literature. 

ME has also been referred to as "fast mapping." We believe that this label is confusing because it conflates two distinct ideas. In an early study, @carey1978 presented children with an incidental word learning scenario by using a novel color term to refer to an object: "You see those two trays over there. Bring me the *chromium* one. Not the red one, the *chromium* one." Those data [and subsequent replications, e.g. @markson1997] showed that this exposure was enough to establish some representation of the link between phonological form and meaning that endured over an extended period; a subsequent clarification of this theoretical claim emphasized that these initial meanings are partial [@carey2010]. Importantly, however, demonstrations of retention relied on learning in a case where there was a contrastive presentation of the word with a larger set of contrastive cues [@carey1978] or pre-exposure to the object [@markson1997]. 

Further, the "fast mapping" label has been the focus of critique due to findings by @horst2008fast that young children do not always retain the mappings that result from the disambiguation inference. <!-- MORE HERE -->


Here we adopt the label "mutual exclusivity" (ME) for the general family of paradigms and associated effects, *without* prejudgment of the theoretical account of these effects.  The ability to make the inference -- via whatever mechanism -- that a novel word maps to a novel object makes the problem much easier to solve. We call this inference the "ME inference".

The ME effect has received much attention in the word learning literature because the ability to identify the meaning of a word in ambiguous contexts is, in essence, the core problem of word learning. That is, given any referential context, the meaning of a word is underdetermined [@quine1960], and the challenge for the world learner is to identify the referent of the word within this ambiguous context. For example, suppose a child hears the novel word "kumquat" while in the produce aisle of the grocery store. There are an infinite number of possible meanings of this word given this referential context, but the ability to make a disambiguation inference would lead her to rule out all meanings for which she already had a name. With this restricted space of possibilities, she is likely to identify the correct referent than if all objects in the context were considered as possible referents. 

Being able to make an ME inference could also help children acquire words for multiple words that can be used to refer to the same object in the world, even though they actually refer to different concepts [for example, property names and object parts such as “turquoise” and “handle"; @markman1988]. Consider a child who hears the novel word “turquoise” in the context of a turquoise-colored ball. If she obeys the one-to-one property of language and already knows the word “ball,” the child may assume that “turquoise” refers to a property of the ball, such as color, rather than the ball itself. Of course, seeing evidence about the meaning of "turquoise" across multiple different turqouise referents situations [referred to as "cross-situational evidence"; @yu2007rapid].

Making ME inferences could be particularly useful for learning subordinate (e.g., “dalmation”) and superordinate labels (e.g., “animal”); Each instance of these labels is always consistent with concepts at all levels of the conceptual hierarchy [an observed dalmation is equally consistent with the labels “dalmation,” “dog” and “animal”; e.g., @waxman1986preschoolers]. Also, and unlike in the case of property words, a child will never observe cross-situational evidence that disambiguates among candidate concepts at different levels of the hierarchy. Thus ME inferences provide one possible route through which children might resolve this inherent ambiguity in word learning. 

Despite -- or perhaps due to -- the attention that the ME effect (and the related consequences of making ME inferences) has received, there is little consensus regarding the cognitive mechanisms underlying it. Does it stem from a basic inductive bias on children's learning abilities ("constraint and bias accounts," "probabilistic accounts," and "logical inference accounts"), a learned regularity about the structure oflanguage ("overhypothesis accounts"), reasoning about the goals of communication in context ("pragmatic accounts"), or perhaps some mixture of these? Across the literature, researchers have tested a variety of populations of children and used a wide range of different paradigms in order to discriminate between these theories, and a successful theory of ME will need to be able to account for this wide range of empirical phenomena.

In the current paper, our goal is to present evidence for one particular pattern of findings related to ME: Developmental change in the magnitude of the effect. Characterizing developmental change in ME is important because it provides a key constraint on theoretical accounts of ME. Namely, change in the magnitude of ME must be due either to maturational change or the child's increasing experience with the word, or both. In our work here, we focus on characterizing the link between developmental change and one type of experience---linguistic experience. There are a variety of ways that linguistic experience could support the ME inference. For example, a child who knows more words in general might be more likely to know the familiar word in the ME task, and therefore more likely to select the novel object. Our aim is not to definitively discriminate between theories of ME, but rather present evidence for a theory-constraining pattern of data. In the General Discussion, we consider in more detail how existing theories of ME might account for our findings.

Across the literature on ME, developmental change has played a relatively minor role in theoretical accounts, with researchers instead focusing on determining whether children behave in a way that is consistent with the ME effect at one or a few timepoints in development. In part, this empirical approach may be due to  methodological challenges in conducting developmental experiments, rather than to theoretical perspectives that are unconcerned with developmental change. This is because data collection from young children is expensive, it is difficult for researchers to collect data from children across more than a couple ages groups. In addition, experimental evidence from the ME paradigm is typically summarized as a binary descprition (children's "success" or "failure" in the ME task), and this methodological choice may obscure evidence for more subtle changes in the cognitive system across development.

There are, however, a handful of studies that show developmental change in the mutual exclusivity effect by testing multiple age groups within the same experiment [e.g., @halberda2003development;@merriman1986some;@bion2013fast]. For example, @halberda2003development tests 14- 16- and 17- mo in the ME paradigm, and finds a pattern of developmental change: 14 mo children are biased to select the familiar object, 16-mo were at chance, and 17-mo were biased to select the novel object, demonstrating the ME effect. While multi-age-group studies such as this  provide clear evidence *that* there is developmental change, they do not provide they type of quantitative description of its developmental trajectory of the effect that could provide an important constraint on theories of ME. 

## The Current Study
We first describe the state of the evidence for developmental change in the ME effect via a meta-analysis of the extant empirical literature. By aggregating across studies that each test different ages, the meta-analytic approach allows us to take advantage of the large number of studies already conducted on the ME effect in order to characterize developmental change. We then present two new, relatively large-sample developmental experiments that investigate the causal role of linguistic experience in contibuting to the ME effect. In Experiment 1, we examine the relationship between vocabulary size and the strength of the ME effect on a large sample of children. We find evidence that children with larger vocabularies tend to show a stronger ME effect, consistent with the notion that language experience influences the ME effect. In Experiment 2, we more directly test the hypothesis that language experience plays a *causal* role in the ME effect, by directly manipulating children's amount of experience with a word. We find greater experience with the familiar word in the ME paradigm leads to a stronger ME effect.  In the General Discussion, we conclude by discussing the role of developmental change and experience in the context of candidate theories of ME, in the context of our evidence.

```{r child = "sections/ma_writeup.Rmd"}
```

```{r child = "sections/exp1_writeup.Rmd"}
```

```{r child = "sections/exp2_writeup.Rmd"}
```

# General Discussion


These three constraints are consistent with many of individual proposed accounts, as well as a various combinations of them. For example, an effect of language experience on the disambiguation effect via vocabulary knowledge is most consistent  with the overhypothesis account, which predicts a stronger learned bias with vocabulary development. However, all four accounts predict developmental change in the NN trials. Under the overhypothesis account, as children are exposed to more language, they develop a stronger learned bias even when the "familiar" word is not previously known; Under the pragmatics account, as children are exposed to more language, they develop more skill in making social inferences, which would led to increased performance on the NN trials; And, under the bias and probabilistic accounts, maturational change could contribute to development in domain-general abilities, leading to a stronger disambiguation inference. Finally, the ability of children to succeed in the disambiguation tasks despite a range of impairments suggests that accounts that rely on a single mechanism, such as pragmatic reasoning or a mutual exclusivity constraint alone, are unlikely to describe the mechanism underlying the disambiguation effect across all children. 


We conclude that:

1. Explanations of ME are not themselves mutually exclusive and likely more than one is at play. <!-- *momen and merriman make this point -->
2. The balance of responsibility for behavior likely changes developmentally, with basic biases playing a greater role for younger children and learned overhypotheses playing a greater role for older children. 
3. All existing accounts put too little emphasis on the role of experience and strength of representation; this lack of explicit theory in many cases precludes definitive tests of mechanism. 

To summarize, the empirical findings that a successful theory of ME must account for are:

(1) Why the effect is present in young children, but gets larger with development (developmental change);
(2) How language experience supports the effect (multilingualism evidence);
(3) Why pragmatic reasoning can support the effect (speaker change evidence), but why it is not necessary (autism evidence). 

## The role of development in theories of the ME effect

What are the cognitive mechanisms underlying the ME effect? A number of proposals have been made in the literature, many of which overlap or differ only in subtle ways. Here we briefly describe several influential proposals, highlighting the commonalities and differences across theoretical views. This review is necessarily selective; in addition in this portion of the manuscript, we engage primarily with qualitative and verbal theories. We return to the issue of computational models that treat the ME effect in a later section. 

### Constraint and bias accounts

One proposal is that children have a constraint or bias that is innate or emerges after very limited language input. Under one version of this account [@markman1988;@markman2003], children have a constraint on the types of lexicons considered when learning the meaning of a new word -- a "mutual exclusivity constraint." Under this constraint, children are biased to consider only those lexicons that have a one-to-one mapping between words and objects. Importantly, this constraint is probabilistic and thus can be overcome in cases where it is incorrect (e.g., property names or super-/sub-ordinate labels), but it nonetheless serves to restrict the set of lexicons initially entertained when learning the meaning of a novel word. In principle, this constraint could be the result of either domain-specific or domain-general processes [@markman1992constraints]. As a domain general property, the ME constraint could be related to other cognitive mechanisms that lead learners to prefer one-to-one mappings (e.g. blocking and overshadowing in classical condition and the discounting principle in motivational research; @lepper1973undermining).

As formulated by Markman and colleagues, the ME constraint operates at the level of extensions (objects), not concepts. For example, the ME constraint says that the labels “policeman” and “cop” -- referring to the same entity in the world -- are violations of the constraint. Similarly, terms at different levels of the semantic hierarchy that can have the same extensions, such as “animal” and “dog,” are also seen as ME violations. In contrast, these cases are not violations in theories that posit the explanatory construct at the level of concepts (e.g., pragmatic accounts). The distinction between concepts and objects in each theoretical view is important for evaluating whether empirical evidence is consistent with a proposal. Note, however, that in the canonical ME paradigm, where the two referents are both different concepts and objects, the accounts at both levels make identical predictions.

A related proposal to the ME constraint is that children have a bias to map novelty to novelty [Novel-Name Nameless-Category principle (N3C); @golinkoff1994early; @mervis1994acquisition]. This principle differs from the ME constraint in that the rejection of the familiar object as a potential referent is not part of the inference; instead, children are argued only to map the two novel elements to each other, the novel label and the object (thereby only implicitly rejecting the the familiar object as a referent for the novel label). The N3C principle is argued to be domain-specific to language.

Under a third account, children are motivated to identify objects for which they do not know a label for and fill the “lexical gap” with the novel label [@golinkoff1992young; @merriman1989mutual].

### Probabilistic accounts

Probabilistic accounts contend that the ME effect does not derive from an explicit representation related to the one-to-one regularity, as proposed by the constraints and bias accounts. Rather, under these accounts, the effect is the product of a word learning system that tracks the frequency of exemplars of words and their referents over time, and then reasons probabilistically about the most likely referent for a novel word within the referential context [@regier2005emergence;@mcmurray2012;@frank2009using;@fazly2010probabilistic;@kachergis2012]. These accounts are typically posed in the context of more explicit computational models and we defer discussion of these until later in the manuscript 

### Pragmatic accounts

Under pragmatic accounts, the ME effect derives from reasoning about the intention of the speaker within the referential context [@clark1987principle; @clark1988logic; @clark1990pragmatics; @diesendruck2001]. The critical aspect of this account is the claim that children assume that “every two forms contrast in meaning” (Clark, 1988, p. 417), or the "Principle of Contrast.” Clark also argues that speakers hold a second assumption -- that speakers within the same speech community use the same words to refer to the same objects ("Principle of Conventionality"). The ME effect then emerges from the interaction of these two principles. That is, the child reason’s implicitly: You used a word I've never heard before. Since, presumably we both call a ball "ball" and if you'd meant the ball you would have said "ball," this new word must refer to the new object. Clark (1988, 1990) argues that these two principles are learned, but emerge from a more general understanding that other people have intentions [@grice1975logic; @tomasello2005search].

### Logical inference accounts

@halberda2003development argues that the ME effect is the result of domain-general processes used for logical reasoning. Under this proposal, children are argued to be solving a disjunctive syllogism (“A or B, not A, therefore B”) by rejecting labels for known objects. For example, upon hearing the novel label “dax,” the child would implicitly reason that the referent could be either object A or B, and then reject object A because it already has a known label. By deduction, the child would then conclude that “dax” refers to object B. This account shares the same formal reasoning structure as pragmatic accounts, but differs in the underlying source of the key inference: While pragmatic accounts argue that children conclude that object B must be the referent on the basis of reasoning about intention, the logical inference account proposes that this same inference is made on the basis of logical reasoning.

### Over-hypothesis accounts

@lewis2013b suggest that the ME effect could emerge by learning from the statistics of the child’s linguistic. That is, given evidence that words tend to refer to a single concept, the child might develop a learned "overhypothesis" [@kemp2007learning] that the lexicon is structured such that each concept is associated with one and only one label. The learning mechanisms are argued to be probabilistic and domain general, while the learned overhypothesis is specific to the structure of the lexicon. The emergent overhypothesis about the structure of the lexicon would be similar to the knowledge a learner is proposed to have under the constraints and biases account. 

In order for learning to get off the ground, however, children must notice the one-to-one mapping between a word and a concept in the context of a particular instances of a label’s usage. @lewis2013b suggest that this ability could derive from a variety of different mechanisms that make use of the structure of the learning task, such as pragmatic, probabilistic, and logical inference accounts. @merriman1986some make a similar proposal, but argue that the overhypothesis is learned primarily from explicit parental corrections (e.g., “that’s an apple, not an orange”).

Under the overhypothesis account, then, the ME effect emerges from multiple mechanisms at two different timescales -- one as a function of information about the pragmatic or inferential structure of the communicative context and one as a function of learned higher-order knowledge about how the lexicon is structured. Both mechanisms would then contribute to the inference with different weights across development and across children.

An important starting point for our analysis is to observe that theoretical accounts of mechanisms underlying the ME effect that have proposed in the literature are not mutually exclusive with each other [@momen2002two]. As argued by @markman1992, testing different mechanisms in isolation is the result of an experimental approach to theory building, rather than a reflection of an assumption that there exists one and only one mechanism underlying the effect. That is, in order to identify whether a mechanism is *sufficient* to give rise to the ME effect, logical researchers design experiments in which the ME effect can be observed only if a particular cognitive mechanism is sufficient for the effect. If the effect is observed under these conditions, it provides evidence only that the mechanism is sufficient for the effect, but not that it is necessary and not that other mechanisms are not also sufficient. Indeed, there is reason to think that redundancy in mechanisms for the same behavior is a desirable property of a cognitive system. 

Instead, we argue that multiple mechanisms likely support the ME effect. Each child may be making use of multiple mechanisms with varying weights across development and situations, and the relative weights of these different mechanisms may vary across children. For example, learners may be making use of both general knowledge about how the lexicon is structured as well as information about the pragmatic or inferential structure of the task, and both of these sources of information support the ME inference.






Potential sources of developmental change
Cognitive limitations mean that you just don’t think of the other object when one is named (Merriman 1986b) - better at coordinating concepts (related to Flavell, though not the same….he actually argues the opposite)..
Perceptual experience - Merriman 1986b
Linguistic input
Mervis 1987 - not till children accept parents authority
Time constraint - Frank (Halberda)



\newpage

# References

```{r session info, include = F}
sessionInfo() %>% pander::pander(compact = F)
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}


---
nocite: | 
@markman1992constraints


```{r}
r_refs(file = "r-references.bib")
render_appendix("appendix.Rmd")
```
