---
title             : "The role of experience in disambiguation during early word learning"
shorttitle        : "Disambiguation during early word learning"

author: 
  - name          : "Molly Lewis"
    affiliation   : "1, 6"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Veronica Cristiano"
    affiliation   : "2"
  - name          : "Brenden Lake"
    affiliation   : "3"
  - name          : "Tammy Kwan"
    affiliation   : "4"
  - name          : "Michael C. Frank"
    affiliation   : "5"
  
affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "Gallaudet University"
  - id            : "3"
    institution   : "New York University"
  - id            : "4"
    institution   : "Cognitive Toybox, Inc."
  - id            : "5"
    institution   : "Stanford University"
  - id            : "6"
    institution   : "University of Wisconsin, Madison"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```


# Introduction

ME is important

ME is controversial 

What do we even call it? 

What's the goal of this paper.

## Theoretical views of "mutual exclusivity"

### Constraint and bias accounts

ME

N3C


### Probabilistic accounts

Regier

McMurray

Frank Goodman Tenenbaum

Fazly


### Over-hypothesis accounts


Lewis & Frank (2013)


### Pragmatic accounts

Clark?

In the moment

Learned pragmatics 

## Theory-constraining findings

NN vs. NF

Speaker-change studies

Autism 

Bilingualism

Fast mapping + no retention

Developmental change (halberda)



## Synthesis

These are definitely features of a successful account:
Timescales
- must be one "in the moment" 
- and one longer-term learned mechanism

Experience

Probabilistic representations

Could be the case also that it's a mixture of pragmatic, etc.


## The current study

Gather evidence on strength of finding

Test emergent relationship to vocabulary (E1)

Test causal relationship to representation strength (E2)

Re-evaluate

# Meta-analysis


## Methods


## Results


## Bilingualism


## Autism Spectrum Disorders



# Experiment 1: ME and Vocabulary


## Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

### Participants

### Material

### Procedure

### Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


## Results and Discussion

Could be specific strength of particular word in the NF pairing

but we also get it for NN trials alone



# Experiment 2: ME and Familiarity


## Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

### Participants

### Material

### Procedure

### Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


## Results and Discussion






# General Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
